### 2023-09-08 Review/response_strategy.Rmd
Création d'un repo git pour les correction de l'article

---
title: "R Notebook"
output: 
  html_notebook:
    toc: yes
    toc_float: yes
    code-fold: yes
---

```{css, echo=FALSE}
pre {
  max-height: 300px;
  overflow-y: auto;
}

pre[class] {
  max-height: 300px;
}

pre, code {white-space:pre !important; overflow-x:scroll !important}

.question {
  text-indent: 5em;
  text-align: justify;
}

.indented_response {
  text-indent: 5em;
  color: #000080;
  text-align: justify;
  margin-bottom: 30px;
}

.response {
  color: #000080;
  text-align: justify;
  margin-bottom: 30px;
  margin-left: 40px
}

.rouge {
  color: red;
  text-align: justify;
  margin-bottom: 30px;
  margin-left: 40px
} 
```

```{r, results = FALSE, cache = TRUE}
library(ggplot2);   library(dplyr);   library(rjags);   library(kableExtra)
```

# Reviewer 1

::: question
In the manuscript 'A hierarchical model to evaluate pest treatments from prevalence and intensity data', Favrot & Makovski present a new and welcome (Bayesian) method for the (meta-)analysis of countable 'infection' units on individual hosts, where the recorded variable may be either the proportion of 'infected' hosts (prevalence) or the mean number of infection units per individual host (intensity), or both quantities. Then, a simulation study is used to demonstrate that intensity data provide more accurate estimates than prevalence data (especially for abundant 'infections'), and to assess the accuracy of the estimates depending on the number of trials. The provided code and convergence seems good. 
:::

::: question
Before starting my comments, I wish to apologize deeply for the inconvenience caused to the authors and editor by the time taken to review the manuscript. Besides, I did not find any line numbering; thus, my comment below only vaguely refer to paragraph or page numbers.
:::

::: indented_response
Ajouter des numéros de lignes dans mes fichiers.
:::

::: question
A general comment : the article focusses on aphid abundance on plants sampled during field trials designed to compare the efficacy of various pest control options, but the framework is more generic (and might be used e.g. in animal/human epidemiology) and the authors may highlight this point in the abstract, introduction and/or discussion.
:::

::: indented_response         
Ajouter une phrase dans la conclusion pour souligner ce point.
:::

## Major comments

::: question
My only methodological comment relates to the choice of a Poisson distribution for W, which is the number of aphids on each plant. Because aphids land and initiate exponentially growing clonal populations at different times on different plants of the same trial x treatment x block x time combination, W should have an overdispersed Poisson distribution (e.g., negative binomial), instead of a Poisson distribution (eq. 1). Thus, Y (the sum of N independent W variables) should not have a Poisson distribution (eq. 3). It would be interesting to test whether an overdispersed Poisson distribution is better than a Poisson distribution for fitting the unaggregated data on the number of aphids on each of the N_i (i.e. 10 here) sampled plants (gaining statistical power from the multiple trials). Although the authors state (in part 2.1) that such data are not available to the authors, these raw data are classically recorded and might be provided by the unspecified colleagues who conducted the field trials (by the way, the institutions that performed the field trials should be mentioned more explicitly).
:::

::: indented_response         
Ce commentaire remet en question le modèle que l'on utilise et propose d'en utiliser un autre : la négative binomiale. La négative binomiale permet de gérer la surdispersion. Ce commentaire nous a fait remarquer que nous n'avions pas vérifié l'ajustement aux données de notre modèle. La première étape sera donc de faire cette vérification. On la fera en appliquant la méthode du "posterior predictive checking", qui consiste, pour chaque observation, à calculer la probabilité que le modèle propose une valeur plus extrême que celle de l'observation considérée. On fera cette vérification uniquement sur les données réelles. La seconde étape sera de coder le modèle reposant sur la loi négative binomiale et de le comparer au modèle de Poisson en utilisant le posterior predictive checking : on fera un scatter plot des proba à posteriori de dépasser les valeurs extrêmes selon les deux modèles (probas d'un modèle en abscisse et probas de l'autre en ordonné).

Notre stratégie de réponse dépendra des résultats de ces deux premières étapes.
:::

[paragraphe biblio pour justifier notre choix]

Nous avons implémenté le modèle négatif binomial sur les données réelles et nous avons comparé son ajustement aux données par rapport au modèle de Poisson, en utilisant la méthode probability posterior checking **[ref]**.

Le modèle est donné par

$$
    W_{ijkts}\sim\mathcal{NB}\big(r,\ \lambda_{ijkt}\big)
$$

Where $\lambda_{ijkt}$ is the mean of $W_{ijkts}$ and $r$ is the overdispersion parameter. The model on $\lambda_{ijkt}$ is the same as the one of the Poisson model, but without the term $\epsilon_{ijkt}$ :

$\begin{align}&\log\ \lambda_{ijkt} = \alpha_0 + \beta_{0i} + \gamma_{0j}  + (\alpha_1 + \gamma_{1j})\ X_t + u_{ij}\label{eq:test}\tag{1}\end{align}$

This settings leads to the following distribution for $Y$ and $Z$ :

$$Y_{ijkt} \sim\mathcal{NB}\big(N_ir,\ N_i\lambda_{ijkt}\big)\ \hspace{1cm} \ Z_{ijkt} \sim \mathcal{B}\big(N_{i},\ \pi_{ijkt}\big)$$

where $\pi_{ijkt} = 1-\big(r\ /\ (r + \lambda_{ijkt})\big) ^ r$ is the probability of $W_{ijkts}$ beeing postitive.

La figure  ci-dessous montre les résultats obtenus pour les deux modèles. On voit que l'ajustement au donné est meilleur avec le modèle de poisson.

![Posterior predictive check](Posterior_predictive_check.png)

![Observed vs predicted values](Observed_vs_predicted_values.png){#fig-Observed_vs_predicted_values_real_data}

<br>
Nous avons aussi vérifié par simulation que notre modèle était pertinent. Nous avons simulé selon le modèle de la négative binomiale puis nous avons inférer avec 2 modèles : 
  - le modèle négative binomiale
  - notre modèle de poisson surdispersé

Le code est donné ci-dessous. Les résultats montre qu'encore une fois le modèle de poisson s'ajuste mieux aux données même si celles si ont été simulé avec le modèle de la négative binomiale.

**Simulation des données**

```{r, cache=TRUE}

source(file = "simu_data_NegB.R")

I = 30
K = 4   # number of blocks
S = 10   # number of beets in the sample

r = 15   # overdispersion parameter

alpha_0 = 0.5
alpha_1 = 0.16

gamma_0 = c(0, - 0.13, - 1.13, - 1.24);  
gamma_1 = c(0, 0.24, - 0.14, - 0.15);

X_t = c(6, 12)

sigma2 = 1.87;  
chi2 = 0.27

set.seed(seed = 1)

data_simu = simu_data_NegB(I = I, K = K, S = S, r = r, alpha_0 = alpha_0, alpha_1 = alpha_1, 
                      gamma_0 = gamma_0, gamma_1 = gamma_1, X_t = X_t, sigma2 = sigma2, chi2 = chi2)

ggplot(data_simu) +
    geom_histogram(aes(x = Y), binwidth = 5)
```

```{r, cache = TRUE}
# Making the two scenarios [100% Z - 0% Y] and [0% Z - 100% Y]
dataZ = data_simu %>% mutate(Y = NA)
dataY = data_simu %>% mutate(Z = NA)
```

**Ecriture des modèles**

```{r, cache = TRUE}
# Negative binomial model

negative_binomial_model = "
model {

    ###################### Likelyhood ######################
    for (i in 1:Q){
        Y[i] ~ dnegbin(p[i], N[i] * r)
        p[i] <- r / (r + lambda[i])

        Z[i] ~ dbinom(pi[i], N[i])
        pi[i] = 1 - p[i] ^ r

        log(lambda[i]) = beta0[TRIAL[i]] + gamma0[TREATMENT[i]] + (alpha1 + gamma1[TREATMENT[i]]) * TIME[i] + u[TRIAL_TREATMENT[i]]

        pred[i] ~ dnegbin(p[i], N[i] * r)            
    }

    for (j in 1:K){
        beta0[j] ~ dnorm(alpha0, invsigma)
    }

    for (c in 1:M){
        u[c] ~ dnorm(0, invchi)
    }

    gamma0[1] = 0
    gamma1[1] = 0

    ######################## Priors ########################
    for (s in 2:L){
        gamma0[s] ~ dnorm(0, 0.001)
        gamma1[s] ~ dnorm(0, 0.001)
    }

    alpha0 ~ dnorm(0, 0.001)
    alpha1 ~ dnorm(0, 0.001)
    sigma ~ dunif(0, 10)
    chi ~ dunif(0, 10)
    r ~ dunif(0, 50)

    ################### Derived Quantities #################
    invsigma = pow(sigma, -2)
    invchi = pow(chi, -2)
}
"

writeLines(negative_binomial_model, con  =  "negative_binomial_model.txt")

# Poisson model

poisson_model = "
model {

    ###################### Likelyhood ######################
    for (i in 1:Q){
        Y[i] ~ dpois(N[i] * lambda[i])
        Z[i] ~ dbinom(pi[i], N[i])
        log(lambda[i]) = beta0[TRIAL[i]] + gamma0[TREATMENT[i]] + (alpha1 + gamma1[TREATMENT[i]]) * TIME[i] + u[TRIAL_TREATMENT[i]] + epsi[i]
        pi[i] = 1 - exp(- lambda[i])
        epsi[i] ~ dnorm(0, inveta)
        pred[i] ~ dpois(N[i] * lambda[i])
    }

    for (j in 1:K){
        beta0[j] ~ dnorm(alpha0, invsigma)
    }

    for (c in 1:M){
        u[c] ~ dnorm(0, invchi)
    }

    gamma0[1] = 0
    gamma1[1] = 0

    ######################## Priors ########################
    for (s in 2:L){
        gamma0[s] ~ dnorm(0, 0.001)
        gamma1[s] ~ dnorm(0, 0.001)
    }

    alpha0 ~ dnorm(0, 0.001)
    alpha1 ~ dnorm(0, 0.001)
    sigma ~ dunif(0, 10)
    chi ~ dunif(0, 10)
    eta ~ dunif(0, 10)

    ################### Derived Quantities #################
    invsigma = pow(sigma, -2)
    invchi = pow(chi, -2)
    inveta = pow(eta, -2)
}
"

writeLines(poisson_model, con  =  "poisson_model.txt")
```

**Inference**

```{r, results = FALSE, cache = TRUE}
# Function to make inference from the data ##########################################################################################
finf <- function(model, df, nadapt, niter){

    Y = df$Y;   Q = length(Y);   N = df$N;   Z = df$Z

    TRIAL = as.numeric(as.factor(as.character(df$trial)));   TREATMENT = as.numeric(as.factor(as.character(df$treatment)));

    TIME = as.numeric(df$X_t);   TRIAL_TREATMENT = as.numeric(as.factor(as.character(df$trial_treatment)));

    K = length(unique(TRIAL));   L = length(unique(TREATMENT));   M = length(unique(TRIAL_TREATMENT));

    # Inférence
    model <- jags.model(file = model, 
                        data = list("Y" = Y, "Z" = Z, "Q" =  Q, "TRIAL" = TRIAL, "TREATMENT" = TREATMENT, "TIME" = TIME, 
                                    "TRIAL_TREATMENT" = TRIAL_TREATMENT, "K" = K, "L" = L, "M" = M, "N" = N), 
                        n.chains = 2, 
                        n.adapt = nadapt)

    samples <- coda.samples(model, variable.names = c("pred"), n.iter = niter, thin = 10)

    return(samples)
}

nadapt = 2000;   niter = 4000
```

```{r, results = FALSE, cache = TRUE}
# Inference with the negative binomiale model, using Intensity
resY_posterior_checking_negative_binomiale = finf(model = "negative_binomial_model.txt", dataY, nadapt = nadapt, niter = niter)

# Inference with the Poisson model, using intensity
resY_posterior_checking_poisson = finf(model = "poisson_model.txt", dataY, nadapt = nadapt, niter = niter)
```

**Comparaison des résultats**

```{r, cache = TRUE}
df_prediction = rbind(

        # negative binomial samples
        cbind(t(resY_posterior_checking_negative_binomiale[[1]]), t(resY_posterior_checking_negative_binomiale[[2]])) %>% 
            as.data.frame %>% mutate(model = "Negative binomial model"),

        # poisson samples
        cbind(t(resY_posterior_checking_poisson[[1]]), t(resY_posterior_checking_poisson[[2]])) %>% 
            as.data.frame %>% mutate(model = "Poisson model")
    ) %>%

    mutate(observation = rep(data_simu$Y, 2)) %>% # 2 for the two models
    mutate(prediction = rowMeans(across(starts_with("V")))) %>%
    mutate(error = (prediction - observation) ^ 2)

ggplot(df_prediction) +
    geom_point(aes(x = observation, y = prediction)) +
    facet_wrap(~ model)
```

```{r, cache = TRUE}
df_prediction %>%
    summarise(MSE = sum(error), .by = model) %>% kbl() %>% kable_styling()
```

```{r, cache = TRUE}
df_prediction %>%
    summarise(MSE = sum(error), .by = model)
```

**MSE sur l'estimation des paramètres**

*En fréquentiste pour réduire le temps de calcul*

```{r mse_simulations, cache = TRUE}
library(lme4)

I_vec = c(30)
seeds = c(1 : 10)

res = NULL

for(I in I_vec){
    for(seed in seeds){

        set.seed(seed)

        data_simu = simu_data_NegB(I = I, K = K, S = S, r = r, alpha_0 = alpha_0, alpha_1 = alpha_1, 
                              gamma_0 = gamma_0, gamma_1 = gamma_1, X_t = X_t, sigma2 = sigma2, chi2 = chi2)

        res_negB = glmer.nb(Y ~ (1|trial) + treatment * X_t + (1|trial_treatment), 
                            data = data_simu)

        res_Poisson = glmer(Y ~ (1|trial) + treatment * X_t + (1|trial_treatment) + (1|ligne), 
                            data = data_simu,
                            family = "poisson")

        MSE_poisson = sum((c(alpha_0 + log(S), gamma_0[- 1], alpha_1, gamma_1[- 1]) - summary(res_Poisson)$coefficients[, 1]) ^ 2)

        MSE_NegB = sum((c(alpha_0 + log(S), gamma_0[- 1], alpha_1, gamma_1[- 1]) - summary(res_negB)$coefficients[, 1]) ^ 2)

        res = rbind(res, data.frame(I = I,
                                    seed = seed,
                                    Model = c("Poisson with OLRE", "Negative binomiale"),
                                    MSE = c(MSE_poisson, MSE_NegB),
                                    Message = c(summary(res_Poisson)$optinfo$message,
                                                summary(res_negB)$optinfo$message),
                                    Warning = c(summary(res_Poisson)$optinfo$warnings %>% length,
                                                summary(res_negB)$optinfo$warnings %>% length)))
    }
}
```

```{r}
ggplot(res) +
    geom_boxplot(aes(y = MSE, x = factor(I), fill = Model))
```

## Minor comments

My other comments are minor and mainly concern typos:

- &#10060; p.3 l.2: 'indeed more time-dependent'

::: response
Ce commentaire fait référence à cette phrase (dans l'introduction) : "measuring intensity is indeed often more time demanding than measuring prevalence, in particular when the pest individuals are small, numerous, and difficult to detect." Je ne comprends pas ce commentaire.
:::

- &#9989; p.3: 'negative impact on a wide range', 'this family of pesticides has been banned', 'some trials may report'

  - &#9989; 'negative impact on a wide range'

  ::: response
  fait référence à la phrase : "Recently, neonicotinoids were recognized as presenting high risks for the environment with a negative impact a wide range of non-target organisms"

  =\> on a oublié le "on", corriger
  :::

  - &#9989; 'this family of pesticides has been banned'

  ::: response
  fait référence à la phrase : "and this familly of pesticides had been banned in several European countries"

  =\> erreur de temps, changer had par has
  :::

  - &#9989; 'some trials may report'

  ::: response
  fait référence à la phrase : "Consequently, for a given pest treatment, some of trials may report prevalence data while others report intensity data"

  =\> le "of" est en trop, corriger
  :::

- &#9989; p.3: 'both types of data', replace 'will' with 'may' (twice)

  - &#9989; ‘both types of data’

  ::: response
  fait référence à la phrase : "while others report intensity data or both type of data"

  => il manque un “s” à “type”, corriger
  :::

  - &#9989; replace ‘will’ with ‘may’ (twice)

  ::: response
  les deux will en questions sont dans la phrase suivante : "It is unclear whether the simultaneous analysis of prevalence and intensity data will increase the accuracy of the estimated treatment efficacy compared to the use of a single type of data, and whether this will increase the probability of identifying the most efficient treatments" =\> faire le remplacement
  :::

- p.3-4: please rephrase this sentence for clarity

::: response
Le reviewer fait référence à cette phrase : "Based on simulations, we then quantify the reduction of mean absolute errors in the estimated treatment efficacies induced by the combination of prevalence and incidence data compared to the use of a single type of data."

Tout d'abord on avait une erreur dans cette phrase : ce n'est pas incidence mais intensity (incidence est synonyme de prévalence).

**Proposition de reformulation** : "Based on simulations, we then quantify the reduction of mean absolute errors in the estimated treatment efficacies induced by using both prevalence and intensity data, compared to the use of exclusively either prevalence or intensity data."
:::

- &#9989; 2.1: 'the Netherlands', 'Intensity and prevalence were monitored at different times after treatments'

  - &#9989; 'the Netherlands'

  ::: response
  fait référence à la phrase : "Data were collected in 32 field trials conducted in France, Belgium and Netherlands to compare several treatments"

  =\> oubli du "the", corriger
  :::

  - &#9989; 'Intensity and prevalence were monitored at different times after treatments'

  ::: response
  fait référence à la phrase : "Intensity and prevalence were monitored at different dates during the growing season."

  =\> remplacer "dates during the growing season" par "times after treatments"
  :::

- &#9989; Fig.1 legend: last 2 sentences are not necessary (obvious or redundant with the figure)

::: response
=\> supprimer ces deux phrases
:::

- &#9989; p.6: 'assuming the Ws are independent', 'quantities used in the model'

  - &#9989; ‘assuming the Ws are independent’

  ::: response
  fait référence à la phrase : "Then, assuming the Ws independent, we have:"

  =\> rajouter "are"
  :::

  - &#9989; ‘quantities used in the model’

  ::: response
  fait référence à la phrase : "The different quantities used by the model are defined in Table 1."

  =\> changer "by" par "in"
  :::

- p.6: a more precise description of model parameterisation is necessary: does the number of sampled plants vary (only) from trial to trial (if yes, subscript i is OK)?

::: response
Oui le nombre de plantes échantillonnées ne varie que selon les essais.

On pourrait modifier la table 1 pour que ce soit plus explicite :

sample size (number of plants) =\> sample size (number of plants), depends only on trials

Do alpha_0 and alpha_1 correspond to the value in the first trial (and first time for alpha_0), or to an average over all conditions?

alpha_0 correspond au nombre moyen (moyenne sur les essais) de puceron dans le groupe non traité le jour de l'application du traitement et alpha_1 correspond à sa dynamique moyenne (sur les essais), toujours dans le groupe non traité.

La définition que l'on a dans la table 1 pour alpha_0 est : "mean number of pest individuals (aphids) in the untreated group"

je propose à la place : "mean of the log number of pest individuals (aphids) over the trials and the blocks, in the untreated group the day of treatment application"

Pour alpha_1, la définition que l'on a dans la tables 1 est : "growth parameter of the number of pest individuals for the untreated group"

Je propose à la place : "mean growth parameter of the number of pest individuals for the untreated group (over trials and blocks)"
:::

- Isn't gamma_1j the treatment effect only at t0?

::: response
Je ne comprends pas ce commentaire, mais il m'a fait voir que la définition du temps n'est pas claire, je propose de remplacer X_t par t

A revoir, il faudrait peut être dire que t=0 peut correspondre soit à la moyenne des temps de mesure, soit au jour du traitement, qu'on peut le définir comme le temps de référence, auquel cas il faut adapter la définition de alpha, il faut aussi que je vérifie qu'il n'y a pas de temps négatif, auquel cas il faudrait mettre des indicatrices dans le modèle
:::

- &#9989; 2.2.2: 'using Bayesian inference', 'to facilitate convergence'

  - &#9989; 'using Bayesian inference'

  ::: response
  fait référence à la phrase "The model parameters were estimated using a Bayesian inference with a Markov chain Monte-Carlo method."

  => supprimer le "a"
  :::

  - &#9989; 'to facilitate convergence'

  ::: response
  fait référence à "and we centered the time variable $t$ to facilitate the convergence."

  => supprimer le deuxième "the"
  :::

- &#9989; p.7: 'extract of the real dataset', 'likelihood'

  - &#9989; 'extract of the real dataset'

  ::: response
  fait référence à "The following code presents the inference on an extract fo the real 
dataset" dans un commentaire de code

  => remplacer "fo" par "of"
  :::

  - &#9989; 'likelihood'

  ::: response
  fait référence à "Likelyood" dans le modèle jags
   => remplacer le "y" par un "i"
  :::

- &#9989; p.11 and thereafter: replace 'subdataset' and 'sub dataset' with 'data subset'

- p.11 and thereafter: why 974 replicates in the simulation study and not, e.g., 1000? Did some replicates fail? Yes, some replicates failed with jags, and due to the computation time, we did not restart the calculations. Should we to it ?

- &#9989; p.12: 'As the computing time is growing', 'Our simulation results'

  - &#9989; 'As the computing time is growing'

  ::: response
  fait référence à "As the calculus time is growing fast" dans un commentaire du code des simulations

  => remplacer calculus par computing
  :::

  - &#9989; 'Our simulation results'

  ::: response
  faité référence à "Our simulations results are obtained" dans le même commentaire.

  => supprimer le "s" de "simulations"
  :::

- &#9989; p.24 l.2: 'identifying'

  ::: response
  fait référence à "for assessing the efficacy of treatments and indentifying"

  => supprimer le premier "n"
  :::

- &#9989; p.26: 'thousands', 'intensity data led to a substantial'

  - &#9989; 'thousands'

  ::: response
  fait référence à "and convergence was quickly achieved after a few thoushands iterations."

  => supprimer le deuxième "h"
  :::

  - &#9989; 'intensity data led to a substantial'

  ::: response
  fait référence à "intensity data let to a substantial reduction of the uncertainty"

  => remplacer "let" par "led"
  :::

# Reviewer 2

Overall, I think this paper is interesting.

**SUMMARY OF THE PAPER**

In a typical experiment for evry trial $i$, treament $j$, block $k$, time $t$ we have three possible scenarios

(1) a measure for both prevalence ($Z_{ijkt}$) and intensity ($Y_{ijkt}$)

(2) a measure for prevalence only ($Z_{ijkt}$);

(3) a measure for intensity only ($Y_{ijkt}$).

In the paper $Y_{ijkt}$ are modelled with a Poisson distribution of mean parameter $\lambda_{ijkt}$ and the with a Binomial distribution of parameter $1-\exp(-\lambda_{ijkt})$.

$\lambda_{ijkt}$ is modelled with a Gaussian distribution whose mean is linear function of four time and treament parameters (see equation (2)).

The inference is done using an MCMC with the rjags package.

## Major Comments

### A.

::: question
Introduction page 2-3. I am not an expert at modeling pest-treatment data, and I trust the authors when they say that modeling both intensity and prevalence is new. The authors state that prevalence or intensity are typically analysed with Binomial or Poisson glm. There are multivariate models for count data (see the three references below, there are many others...). These are not discussed in the introduction. It is my strong opinion that they should (even if adapting these approaches to model intensity/prevalence is outside the scope of this paper).

[1] https://www.sciencedirect.com/science/article/abs/pii/S0165176500002251 Gurmu, Shiferaw, and John Elder. "Generalized bivariate count data regression models." Economics Letters 68.1 (2000): 31-36.

[2] https://link.springer.com/article/10.1007/s00180-018-0828-5#ref-CR24 Osiewalski, Jacek, and Jerzy Marzec. "Joint modelling of two count variables when one of them can be degenerate." Computational Statistics 34 (2019): 153-171.

[3] https://journals.sagepub.com/doi/abs/10.3141/2019-01?journalCode=trra Park, Eun Sug, and Dominique Lord. "Multivariate Poisson-lognormal models for jointly modeling crash frequency by severity." Transportation Research Record 2019.1 (2007): 1-6.
:::

::: response         
=> Lire ces articles et voir si on peut y faire référence dans l’introduction
:::

### B.

::: question
The reason why it does make sense to consider some parameters as fixed and others as random is not very clear to me. It is stated, that this model was validated in another study (Laurent et. al 2023). As far as I can tell the main focus of the Laurent et. al 2023 was not to validate this model. I think a few high-level explanations would ease reading. It would also be usefull to cite in which sections/paragraphs of Laurent et. al 2023 equation (2) is validated.
:::

::: response
Ce commentaire fait référence à la partie suivante :
:::

$$
	\log\ \lambda_{ijkt} = \alpha_0 + \beta_{0i} + \gamma_{0j}  + (\alpha_1 + \gamma_{1j})\ X_t + u_{ij} + \epsilon_{ijkt} \tag{2}
$$

with

- $\beta_{0i}\sim\mathcal{N}(0, \sigma_0^2)$
- $u_{ij}\sim\mathcal{N}(0, \chi^2)$
- $\epsilon_{ijkt}\sim\mathcal{N}(0,\eta^2)$

*The random variables are all assumed independent. The combination of fixed and random effects used in Equation 2 has been validated in a previous study (Laurent et al. (2023)).*

The observed variables (intensity and prevalence) can be expressed as a function of $W$. We note: ...

::: response
paramètre lié au site qui sont random, on ne veux pas faire d'inférence site par site, on veut faire une inférence pour la population de site, globale, choix qui dépend de l'obejctif de l'inférence, par rapport à la population de site

Annabelle a fait des comparaison de modèle avec l'AIC, terme validé ambigu. Pour le choix entre fixe et random, meme si fixe et random ne font normalement pas référence aux lois mais au fait que le paramètre soit commun à tous les individus ou pas. Mais pour paler de la loi (constante ou aléatoire), on prend constant quand on veut estimer et aléatoire quand on n'en a pas besoin on prend aléatoire.
:::

### C.

::: question
Page 10, I understand that in some trials only Y or only Z data are available. I was not able to understand how this was modelled. Missing at random?
:::

::: resonse
aléatoire, réexpliquer mieux certains scénarios des simulations

En fait je ne comprends pas ce commentaire, peut etre faut il redire que quand on enlève des Z, on n'a pas le choix, ce sont des Z que l'on a pas, et là je ne sais pas quel mécanismme fait que les Z n'ont pas été collecté dans ces sites, et puis d'ailleurs, faut il toujours modéliser les NAs ? je vois pas très bien ce que veut dire "modéliser un NA". Quant au Y, quand on en a enlevé, on a enlevé ceux pour les quels Z a été mesuré (on a pris le complémentaire), ce qui se discute, on aurait pu tirer au hasard les sites ou enleve Y, ou alors prendre les meme que Z pour mieux comparés. en vérité j'ai du quand meme enlevé quelques Z qu'on avait, j'ai fait ça pourque le nombre d'observation soit à peu pres similaire entre Y et Z pour les 50%    
:::

### D.

#### D.0.

As stated in the paper "the prevalence data are usually more accessible in practice and the intensity data more costly".

To better compare and discuss the results it would be important to get a sense of these costs. For example, if it is 10 times more costly to get Y for one trial then comparing [50% Y - 0% Z] to [0% Y - 50% Z] does not seem exactly fair.

::: response
=\> Pour moi ce n'était pas le but de l'article d'approfondir cette question du coût et de l'optimisation qui en découle, étant donné que l'on a pas cette information. En fait je pense que ça pourrait faire partie d'une limite de l'article dont on parlerait dans la conclusion. Stratégie de réponse : en parler dans la conclusion.

on ne connait pas exactement le cout, on a pas une estimation précise de la différence, demander à Fabienne ou cédric, on ne peut pas trop diminuer le nb d'essait avec Y, sinon on a plus assez d'essai

on pourrait utiliser notre modèle pour faire de l'optimisation de design, quand on connait les cout
:::

#### D.1.

::: question
In table 2 and 3, I think it would be clearer to always specificy the amount for Y and Z. For example [100% Y - 0% Z], [50% Y - 0% Z], ...

For now, I am not exactly sure which datasets are considered. This might explain some of the other questions I have…
:::

::: response         
=> faire la modification proposée
:::

#### D.2.

::: question
I am not sure I understand the choice of the 4 subdatasets in table 2. Would it not make sense to consider all the scenarios of table 3? In particular why not [100% Y - 100% Z] and [0% Y - 100% Z]?
:::

::: response         
=\> On ne peut pas faire ça car on ne dispose des Z que dans 15 essais sur les 32 (paragraphe 2.1)
:::

Based on D0) why not consider more intermediate levels of Y : [25%Y - 100% Z], ...

::: response         
on voulait surtout illustrer le principe des modèle et montrer que le design a un impact, et que notre modèle peut etre appliqué pour de l'optimisation
:::

### E.

::: question
As I already stated I am not an expert at modeling this type of data, but it feels that the number of plants is an important parameter. The larger it is the better the Z variable should be? I am not sure why this is not considered in the simulations.
:::

::: response         
il n'y pas de design optimal, il faut un point de départ, l'optimum dépend du parametre des modèles, on a fait des simus sur la base des paramètres inférés sur le s données réelles qui correspondent à des conditions spécifiques : on peux optimiser un design futur

C'est vrai, plus le nombre de plantes est grand, plus la précision que Z apporte est grande. On ne l'a pas considéré pour des raisons de simplicité et de temps de calculs.

Stratégie de réponse : proposer d'en parler dans la conclusion, dire que cela pourrait faire partie d'un problème d'optimisation. On pourrait par exemple, étant donné N_y la taille d'échantillon pour laquelle on mesure l'intensité, chercher N_z la taille d'échantillon pour laquelle on mesure la prévalence qui soit telle que la précision obtenue avec l'intensité soit égale à la précision obtenue avec la prévalence.

notre objectif n'éatit pas de faire une optimisation absolue du modèle,
:::

::: question
In terms of experimental design, depending on the cost of $Y$ and $Z$, increasing the number of plants (rather than measuring the intensity) might very well be a better option?
:::

::: response         
Oui, voir la réponse précédente, il doit exister un $N_z = f(N_y)$ tel que la précision obtenue avec $Y$ soit égale à celle obtenue avec $Z$.

Stratégie de réponse : proposer d’en parler dans la conclusion
:::

### F.

::: question
I imagine one reason to consider a limited number of scenarios is computationnal runtime? If so, this should be stated?
:::

::: response         
=\> Oui, stratégie de réponse : parler du temps de calculs pour justifier le nombre limité de scénarios considérés
:::

### G.

::: question
For section 3.1.2, when discussing the size of the credibility intervals in Figure 4. As far as I understand the conclusions are based on one subsample of the whole data, is it? If so, I think subsampling should be repeated, to argue that in general (that is over a large number of subsamples) the credibility intervals are smaller with a particular sub-dataset ([50% Y - 0 % Z], [0% Y - 50 % Z]....)
:::

::: response         
=\> Oui, ces résultats sont basés sur un seul extrait du jeu de données

Stratégie de réponse : faire d'autres sous-échantillons et voir les résultats que cela donne, en terme de taille d'intervalles de crédibilités mais aussi de consistance dans l'estimation de l'efficacité

on a le choix que pour 50% Y, pour les autres pas le choix vu que Z est manquant d'office, et que justement ces résultats sont confirmés par les simulations
:::

## Minor comments

::: question
a)  Would it not be simpler mathematically to model Ni-Zijkt to have a binomial of parameter exp - ijkt
:::

::: question 
b)  In the model specification, some parameters are given without priors. I suppose they are considered as fixed? This should be stated.
:::

::: question
c)  In table 2 why 15 trials for Z and 17 for Y?
:::

# Reproducibility

::: question
Another important point for publication in Computo is reproducibility. We appreciate your efforts to make the code available, and to include in the article an example of real data analysis and simulated data. However, several points need to be addressed to improve reproducibility. These points are listed in : https://github.com/armandfavrot/mysubmission/issues/1 I made a pull request in order for you to easily include the changes I proposed to your repository: https://github.com/armandfavrot/mysubmission/pull/2 Feel free to contact me for any question about reproducibility: the Computo team will assist you if needed.
:::

**Points listed in the github issue :**

- availability of the experimental data (e.g. from a zenodo repository)

- &#9989; the code to reproduce all figures in the paper (including Fig 1) should be provided

::: response
done, j'ai mis les données nécessaire aux figures dans /data/
cf commit "Point 2 of the reproducibility issue on github - adding code for Fig1" (20baac3981175f2692234ae65d58b14eb87504fa)
:::

::: rouge
il faudra que je mette toutes les données extérieures dans data ? revoir le dossier Files_for_code ?
:::

- the results presented in tables should be generated from the output files (e.g. usign knitr::table)

::: response
J'ai fait ça pour les tables 4, 5, 6 et 7. 
:::

::: rouge
Problème : le symbole "%" ne passe pas dans les titres (cela concerne les figures 4 et 5)
:::

- &#9989; the R package renv should be used in order to ensure the reproducibility of the envirionment used to generate your results

::: response
done, j'ai juste installer le package renv et j'ai exécuté la commande renv::init() à la racine du dossier mysubmission.
cf commit "Point 4 of the reproducibility issue on github - using renv", (831c82945dd6ce21fa88b861ea24ca9eb3a244b6)
:::

- &#9989; rather than copying source code from the R package 'coda' in (https://github.com/armandfavrot/mysubmission/blob/master/Files_for_code/Functions.R), please use the package functions directly (only gelman.plot2 should remain)

::: response
cf commit "Points 5 and 6 of the reproductibility issue on github" (3c13239edfa017f6deac8feb6110d8b257542121) sur la branche correction_2.

J'ai dû garder le code source de certaines fonctions du package 'coda' (fonctions non disponible avec "library(coda)"). J'ai mis l'ensemble de ces fonctions dans /functions/gelman.R (source : https://rdrr.io/cran/coda/src/R/gelman.R).
:::

- &#9989; in order to ensure that the same code has been used in the examples given in the article (chunks 'inference_example_real_data' and 'simulations'), please
  - store this code in external files (funtions in a subfolder 'functions')
  - include these files from the article source
  - add to the repository scripts to reproduce the full analysis (e.g. in a subfolder 'scripts'

::: response
cf commit "Points 5 and 6 of the reproductibility issue on github" (3c13239edfa017f6deac8feb6110d8b257542121) sur la branche correction_2
:::

- &#9989; prefer using .rds files (with readRDS/saveRDS) rather than .Rdata files (with load/save): loading .Rdata file may have the undesired side effect of overwriting existing R variables.

::: response
J'ai changé tous les .Rdata en .rds.
cf commit "Point 7 of the reproducibility issue on github" (187b404487f184de376032881b86006eb77d5b6b) sur la branche correction_2
:::

- you may turn important code comments into notes

**Example for storing code in external file and using this code in the article:**

https://github.com/pneuvial/computo-2023-favrot/blob/reproducibility/Article.qmd#L350-L354

**Example for turning important code comments into notes:**

https://github.com/pneuvial/computo-2023-favrot/blob/reproducibility/Article.qmd#L356-L366

# Temporary notes

## Problème d'optimisation

On veut trouver le design de l'expérience qui maximise la précision de l'estimation de l'efficacité, sous diverses contraintes, dont le côut du design.

Notations :

- $I_Y$ : nombre d'essais où on mesure $Y$
- $I_Z$ : nombre d'essais où on mesure $Z$
- $I = I_Y + I_Z$ : nombre total d'essais
- $N_Y$ : nombre de betteraves sur lesquelles on compte $Y$
- $N_Z$ : nombre de betteraves sur lesquelles on compte $Z$
- $K$ : nombre de blocs dans chaque essai
- $T$ : nombre de dates d'observation pour chaque essai

- $x = (I_Y, I_Z, N_Y, N_Z, K, T)$ : design de l'expérience

- $u(x)$ : coût du design
- $f(x)$ : précision du design

- $\mathcal{S} = \{x\ |\   u \le U_{max},\ I \ge I_{min},\ N_Y \ge N_{min},\ N_Z \ge N_{min},\ K = 4,\ T = 3\}$ : **ensemble de contraintes**

\
On cherche $x^* \in \mathcal{S}$ tel que

$$f(x^*) = \max_{x \in \mathcal{S}} f(x)$$

Intuition : $I_Z^* = 0$ ou $I_Y^* = 0$

### 2023-09-08 Article/Article.qmd
Création d'un repo git pour les correction de l'article

---
title: "A hierarchical model to evaluate pest treatments from prevalence and intensity data"
author:
  - name: "Armand Favrot"
    corresponding: true
    email: armand.favrot@inrae.fr
    affiliations:
      - name: MIA Paris-Saclay, INRAE AgroParisTech Université Paris-Saclay, France
        url: https://mia-ps.inrae.fr/
  - name: "David Makowski"
    corresponding: true
    email: david.makowski@inrae.fr
    affiliations:
      - name: MIA Paris-Saclay, INRAE AgroParisTech Université Paris-Saclay, France
        url: https://mia-ps.inrae.fr/
date: last-modified
description: |

abstract: >+
  In plant epidemiology, pest abundance is measured in field trials using metrics assessing either pest prevalence (fraction of the plant population infected) or pest intensity (average number of pest individuals present in infected plants). Some of these trials rely on prevalence, while others rely on intensity, depending on the protocols.

  In this paper, we present a hierarchical Bayesian model able to handle both types of data. In this model, the intensity and prevalence variables are derived from a latent variable representing the number of pest individuals on each host individual, assumed to follow a Poisson distribution. Effects of pest treaments, time trend, and between-trial variability are described using fixed and random effects.

  We apply the model to a real dataset in the context of aphid control in sugar beet fields. In this dataset, prevalence and intensity were derived from aphid counts observed on either factorial trials testing different types of pesticides treatments or field surveys monitoring aphid abundance.

  Next, we perform simulations to assess the impacts of using either prevalence or intensity data, or both types of data simultaneously, on the accuracy of the model parameter estimates and on the ranking of pesticide treatment efficacy.

  Our results show that, when pest prevalence and pest intensity data are collected separately in different trials, the model parameters are more accurately estimated using both types of trials than using one type of trials only. When prevalence data are collected in all trials and intensity data are collected in a subset of trials, estimations and pest treatment ranking are more accurate using both types of data than using prevalence data only. When only one type of observation can be collected in a pest survey or in an experimental trial, our analysis indicates that it is better to collect intensity data than prevalence data when all or most of the plants are expected to be infested, but that both types of data lead to similar results when the level of infestation is low to moderate. Finally, our simulations show that it is unlikely to obtain accurate results with fewer than 40 trials when assessing the efficacy of pest control treatments based on prevalence and intensity data.

  Because of its flexibility, our model can be used to evaluate and rank the efficacy of pest treatments using either prevalence or intensity data, or both types of data simultaneously. As it can be easily implemented using standard Bayesian packages, we hope that it will be useful to agronomists, plant pathologists, and applied statisticians to analyze pest surveys and field experiments conducted to assess the efficacy of pest treatments.

keywords: [bayesian model, epidemiology, hierarchical model, pest control, trial, survey]
doi: "to complete"
citation:
  type: article-journal
  container-title: "Computo"
  issued: "2023/01/25"
  url: https://computo.sfds.asso.fr/
  issn: "2824-7795"
google-scholar: true
bibliography: references.bib
github-user: computorg
repo: "To complete"
draft: false 
published: false
format:
  computo-pdf: default
---

```{r dependencies, cache = FALSE, include = FALSE}
library(ggplot2);
library(tidyverse);
library(gridExtra);
library(rjags);
library(latex2exp);
library(grid);
library(dplyr);
library(tidyr);
library(tibble)
library(kableExtra)
library(coda)

x = 6;   y = 8;   z = 7
theme_replace(axis.text = element_text(size = x),   axis.title.x = element_text(size = y), 
              axis.title.y = element_text(size = y, angle = 90, margin = margin(r = 5)),
              strip.text = element_text(size = z, face = "bold", color = "white"),
              legend.text = element_text(size = y), legend.title = element_text(size = y, face = "bold"),
              plot.title = element_text(size = z, hjust = 0.5, face = "bold"),
              strip.background = element_rect(fill = "#4345a1"), panel.background = element_rect(fill = "#f3faff"), panel.grid.major = element_line(colour = "white"))
options(ggplot2.discrete.fill = list("#67c5a7"))
```

# Introduction

In plant epidemiology, pest and disease presence can be measured in a host population using different metrics. A first metric measures the presence/absence of the pest in the individuals (plants) of the host population. This metric is often called prevalence or incidence (@madden1999sampling, @shaw2018metrics). The prevalence describes the proportion of the host population in which the pest is present. This metric is relevant and widely used, but it does not account for the number of pest individuals per host individual. With the prevalence, a plant infected by one single pest individual (e.g., an insect) and a plant infected by many pest individuals both represents one infected plant. For this reason, pest abundance is sometimes assessed using another metric representing the average number of pest individuals per host individual. This metric is called intensity or severity (@madden1999sampling, @shaw2018metrics), and describes the intensity of the disease in the target population. These two metrics do not generally have the same requirement in terms of working time; measuring intensity is indeed often more time demanding than measuring prevalence, in particular when the pest individuals are small, numerous, and difficult to detect.

Pest prevalence and intensity are commonly measured in factorial field trials to test the efficacy of different treatments. In this paper, we place ourselves in an important application framework which is the evaluation of alternative pesticide treatments to neonicotinoids against aphids in sugar beet. Indeed, neonicotinoids had been a popular chemical treatment to control aphids for many years, especially in sugar beets, a major crop in Europe. Recently, neonicotinoids were recognized as presenting high risks for the environment with a negative impact on a wide range of non-target organisms, including bees (@wood2017environmental, @pisa2015effects), and this familly of pesticides has been banned in several European countries. In order to find a substitute to neonicotinoids, a number of factorial field trials were conducted to compare the efficacy of different alternative treatments during several years in different countries. Each trial consists of a set of plots divided into several blocks, themselves divided into several strips on which different pesticide treatments are randomly allocated. One strip always remains untreated to serve as a control. In each strip, aphid prevalence, aphid intensity or both metrics are measured in a sample of plants (usually, 10-20 plants per strip).  Depending on the protocol and on the working time constraint, either one type or both types of metrics are measured. Consequently, for a given pest treatment, some trials may report prevalence data while others report intensity data or both types of data. 
    This heterogeneity raises several issues. A first issue concerns the statistical analysis of the trials reporting prevalence and intensity. Although it is easy to fit a generalized linear model to each type of data separately, it is less straightforward to fit a single model to the whole set of trials in order to obtain a single ranking of the pest treatements taking into account both types of data at the same time. Generally, factorial trials assessing treatment efficacy are analyzed with statistical models that take into account one of the two metrics but not both. Prevalence data are thus commonly analyzed using binomial generalized linear models and intensity data are frequently analyzed with Poisson generalized linear models (@michel2017framework, @LAURENT2023106140, @agresti2015foundations). As far as we know, no statistical model has been proposed to assess treatment efficacy based on the simultaneous analysis of prevalence and intensity data.
    Another issue concerns the practical value of combining both prevalence and intensity data. It is unclear whether the simultaneous analysis of prevalence and intensity data may increase the accuracy of the estimated treatment efficacy compared to the use of a single type of data, and whether this may increase the probability of identifying the most efficient treatments. Finally, it is also unclear how future trials should be designed, in particular how many trials are required to obtain accurate estimations, and whether intensity data should be prefered to prevalence data.

 In this paper, we propose a new flexible statistical model that can be used to rank pest treatments from trials including prevalence data, intensity data, or both. We apply it to a real dataset including trials testing the efficacy of pesticides against aphids infesting sugar beets, considering contrasted scenarios of data availability, and we show how the proposed model can be used to evaluate the efficacy of different treatments. Based on simulations, we then quantify the reduction of mean absolute errors in the estimated treatment efficacies induced by the combination of prevalence and incidence data compared to the use of a single type of data. The rest of the paper is organized as follows. First, we present the structure of the dataset including real prevalence and intensity data. Next, we describe in detail the proposed model, the inference method, and the simulation strategy. After checking the convergence of the fitting algorithm, we show how the model can be used to assess treatement efficacy. We finally present the results based on simulated data and we make several recommendations.

# Material and Method

## Desciption of the data

Data were collected in 32 field trials conducted in France, Belgium and the Netherlands to compare several treatments against aphids in sugar beets. Each trial consists in a plot located in a given site at a given year (site-year) divided into one to four blocks. Each of these blocks is itself divided into strips where different treatments are tested, one of these treatments being an untreated control and the others corresponding to different types of insecticide. In each strip of each block, the number of aphids was counted on a sample of 10 beet plants (intensity). The number of infested plants (prevalence) was measured as well, but only in 15 trials out of 32. The total numbers of intensity and prevalence data are equal to 1128 and 561, respectively. Note that the number of aphids was not counted on each beet plant but in the whole plant sample. Intensity and prevalence were monitored at different times after treatments. As shown in @fig-one A, the dataset is unbalanced as less data are available for the treatment Mavrik-jet compared to the others. Figure 1B shows that the intensity and prevalence tend to increase with time.

```{r, fig.width=12, fig.height=14}
#| echo: false
#| label: fig-one 
#| fig-cap: "Description of the dataset. **A** Number of observations according to the type of insecticide. **B** Examples of observed number of aphids averaged over the blocks (intensity) and number of infested beets out of ten (prevalence) averaged over the blocks, at different dates for two trials."

data_figure_1A = readRDS(file = "data/data_figure_1A.rds")
data_figure_1B = readRDS(file = "data/data_figure_1B.rds")

rectangle_fig1A <- grobTree(rectGrob(gp = gpar(fill = "#e9e9e9")), textGrob("A", x = 0.5, hjust = 0.5, gp = gpar(cex = 2.5, fontface = "bold")))

fig1A = ggplot(data_figure_1A) + 
    geom_bar(aes(x = Insecticide, y = n, fill = Insecticide), stat = "Identity") + 
    xlab("Insecticide") + 
    ylab("Number of observations") +
    scale_fill_manual(values = c('#df626c', '#893f3d', '#ff842e', '#188038')) + 
    scale_x_discrete(limits = c("Untreated", "Mavrik Jet", "Movento", "Teppeki")) + 
    theme(legend.position = "none", 
          axis.title.x = element_text(margin = margin(b = 50, t = 20), size = 18),
          axis.title.y = element_text(size = 18, margin = margin(r = 20)),
          axis.text = element_text(size = 16))

rectangle_fig1B <- grobTree(rectGrob(gp = gpar(fill = "#e9e9e9")), textGrob("B", x = 0.5, hjust = 0.5, gp = gpar(cex = 2.5, fontface = "bold")))

fig1B_aphid_intensity = ggplot(data_figure_1B) + 
    geom_point(aes(x = DPT, y = Ymean, col = Insecticide), size = 2.5) + 
    geom_line(aes(x = DPT, y = Ymean, col = Insecticide), size = 0.2) +
    scale_color_manual(values = c('#893f3d', '#ff842e', '#188038')) + 
    facet_wrap(~ ID, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    xlab("") + 
    ylab("Number of aphids") +
    theme(plot.margin = margin(t = 40, r = 40, b = 0, l = 10), 
          axis.title.x = element_text(size = 18),
          axis.title.y = element_text(size = 18, margin = margin(r = 20)),
          axis.text = element_text(size = 16),
          strip.text = element_text(size = 20),
          legend.title = element_text(size = 18),
          legend.text = element_text(size = 18))

fig1B_aphid_prevalence = ggplot(data_figure_1B) + geom_point(aes(x = DPT, y = Zmean, col = Insecticide), size = 2.5) + 
    geom_line(aes(x = DPT, y = Zmean, col = Insecticide), size = 0.2) +
    scale_color_manual(values = c('#893f3d', '#ff842e', '#188038')) + 
    facet_wrap(~ ID, ncol = 2, scales = "free_x") + theme(legend.position = "none") + 
    xlab("Days post treatment") + 
    ylab("Number of infested beets") +
    theme(panel.spacing = unit(1, "cm")) +
    theme(plot.margin = margin(t = 0, r = 40, b = 0, l = 10), 
          axis.title.y = element_text(size = 18, margin = margin(r = 20)),
          axis.text = element_text(size = 16),
          axis.title.x = element_text(margin = margin(b = 20, t = 20), size = 18),
          strip.text = element_text(size = 20))

legend <- cowplot::get_legend(fig1B_aphid_intensity)

do.call("grid.arrange", 
        c(list(rectangle_fig1A, 
               fig1A + theme(plot.margin = margin(t = 30, r = 20)), 
               rectangle_fig1B, 
               fig1B_aphid_intensity + theme(legend.position = "none"),
               fig1B_aphid_prevalence), list(legend), list(ncol = 1, 
             layout_matrix = rbind(c(1), c(2), c(3), c(4), c(5), c(6)), heights = c(0.12, 1.2, 0.12, 1, 1, 0.12))))
```

## Model
### Specification

We introduce an unobserved variable representing the number of pest individuals (here, aphids) on each plant in a sample of $N$ plants (here, sugar beets). This variable is noted $W$ and is assumed to follow a Poisson probability distribution whose mean value is a function of time.

We use the following indexes: $i$ for the trial, $j$ for the treatment, $k$ for the block, $t$ for the time and $s$ for the plant number. The distribution of $W_{ijkts}$ is defined as:

$$
    W_{ijkts}\sim\mathcal{P}(\lambda_{ijkt})
$$ {#eq-model_W}

$$
	\log\ \lambda_{ijkt} = \alpha_0 + \beta_{0i} + \gamma_{0j}  + (\alpha_1 + \gamma_{1j})\ X_t + u_{ij} + \epsilon_{ijkt} 
$$ {#eq-model_lambda}

with

- $\beta_{0i}\sim\mathcal{N}(0, \sigma_0^2)$
- $u_{ij}\sim\mathcal{N}(0, \chi^2)$
- $\epsilon_{ijkt}\sim\mathcal{N}(0,\eta^2)$

The random variables are all assumed independent. The combination of fixed and random effects used in @eq-model_lambda has been validated in a previous study (@LAURENT2023106140).

The observed variables (intensity and prevalence) can be expressed as a function of $W$. We note:

- $Y_{ijkt}$ the number of pest individuals (aphids) in the sample of $N_i$ plants collected in trial i, treatment j, block k, at time t 
- $Z_{ijkt}$ the number of infested plants among the $N_i$ plants collected in trial i, treatment j, block k, at time t

Then, assuming the $W$s are independent, we have:

$$
	Y_{ijkt} = \sum\limits_{s = 1}^{N_i} W_{ijkts}\ \hspace{1cm}\ Y_{ijkt} \sim \mathcal{P}(N_{i}\lambda_{ijkt})
$$ {#eq-model_Y}

$$
	Z_{ijkt} = \sum\limits_{s = 1}^{N_i} \boldsymbol{1}_{W_{ijkts}>0}\ \hspace{1cm} \ Z_{ijkt} \sim \mathcal{B}(N_{i},\ \pi_{ijkt})
$$ {#eq-model_Z}

where $\pi_{ijkt} = 1-\text{exp}(-\lambda_{ijkt})$. The different quantities used in the model are defined in Table 1.

| | |
--|--
i | trial index
j | treatment index
k | block index
t | time index
s | plant index
$N_i$ | sample size (number of plants)
$\lambda_{ijkt}$ | mean number of pest individuals (aphids) on one plant
$\pi_{ijkt}$ | probability for a plant to be infested
$\alpha_0$ | mean number of pest individuals (aphids) in the untreated group
$\beta_{0i}$ | trial effect
$\gamma_{0j}$ | treatment effect
$\alpha_1$ | growth parameter of the number of pest individuals for the untreated group
$\gamma_{1j}$ | treatment effect over time
$X_t$ | number of days post treatment
$u_{ij}$ | random interaction between trial and treatment
$\epsilon_{ijkt}$ | residuals

:  Description of the indices, inputs and parameters used in the model {tbl-colwidths="[15,85]"}

From this model we defined the efficacy of the $j$th treatment at time $t$ ($t$ days after pesticide application) by the quantity (@LAURENT2023106140):

$$
	\text{Ef}_{jt} = \Big(1 - \text{exp}\big(\gamma_{0j}+\gamma_{1j} \times X_{t}\big)\Big) \times 100
$$ {#eq-Efficacy}

The quantity $\text{Ef}_{jt}$ corresponds to the expected percentage reduction of pest individuals (aphid numbers) for the jth treatment compared to the untreated group, over trials and blocks.

### Inference on real data

The model parameters were estimated using Bayesian inference with a Markov chain Monte-Carlo method. We performed the inference using R, with the package rjags (@rjags). For each of the six dataset listed in Table 2, we fitted the model (@eq-model_lambda - @eq-model_Z) with the following weakly informative priors: $\mathcal{N}(0, 10^3)$ for the parameters $\alpha_0,\ \gamma_0,\ \alpha_1,\ \gamma_1$ and $\mathcal{U}([0, 10])$ for the parameters $\sigma_0, \chi, \eta$. We used two Markov chains with $2 \times 10^5$ iterations (after an adaptating phase of $10^5$ iterations), and we centered the time variable $t$ to facilitate convergence.

The convergence of the MCMC algorithm was checked by inspecting the mixing of the two Markov chains and monitoring the Gelman-Rubin diagnosis statistics (@gelman1992inference). We then computed the posterior mean of the pesticide treatment efficacy (defined by @eq-Efficacy) as well as its 95% credibility interval. The code used to fit the model is provided below.

::: {.callout-note}
The following code presents the inference on an extract of the real 
dataset, which includes both trials of figure 1B (2020 - B1A97 ; 2020 - 
u1CwE). It is  a demo for the "50% Y / 50% Z" scenario and we set here the 
number of adaptation and iteration to 2000 in order to reduce computation 
time.
:::

```{r inference_example_real_data, cache = TRUE, results = 'hide'}
#| echo: true
#| eval: false
#| file: scripts/inference_example_real_data.R
```

\
In practice, it is common that only $Y$ or $Z$ data are available in some of the trials. In this case, the resulting dataset includes observations of $Y$ in some trials and observations of $Z$ in others. The dataset may even include one type of observations only, either $Y$ or $Z$, in all trials. Here, we define four scenarios with contrasted levels of $Y$ and $Z$ availability in order to evaluate the consequences of using different types of datasets. We consider four datasets including trials with observations of $Y$, with observations of $Z$, or with both types of observation in different proportions (Table 2). The dataset "100% Y" includes Y data collected in the 32 trials. The dataset "50%Y" includes Y data collected in the 17 trials for which no Z observation is available. The dataset "50% $Z$" includes the Z data collected in the 15 trials for which Z observations are available. The dataset "50% $Y$ - 50% $Z$" includes $Y$ data collected in 17 trials and $Z$ data collected in the other 15 trials. The later dataset does include any trial reporting both $Y$ and $Z$ data.

The hierarchical model defined above is fitted to each dataset in turn. Each fitted model is then used to compute the posterior mean and 95% credibility interval of $Ef_{jt}$ for each treatment at $t$=6 and 12 days after pesticide application.

| Type of dataset | Description |
|---------|:-----|
| 100% Y      | Y observations available in the 32 trials   |
| 50% Y     | Y observations available in 17 trials and no Z  | 
| 50% Z       | Z observations available in 15 trials and no Y    | 
| 50% Y / 50% Z       | Y observations available in 17 trials and Z observations available in the other 15 trials   |

: Four data subsets defined from the original dataset (real data). {tbl-colwidths="[35,65]"}

### Simulations

Simulations are carried out to further investigate the impact of the type and amount of data available on the accuracy of the parameters and the ability of the model to identify the most and least effective treatments.

We define three numbers of trials, equal to 20, 40 and 80, successively. For data simulations, the model parameters are set equal to those estimated from the real dataset "100% Y" defined in Table 2 (posterior means). For each number of trials, we generate virtual data from the model (@eq-model_W - @eq-model_Z) and estimate the model parameters, according to the following procedure:

- Draw values of $\beta_{0i},\ u_{ij}$ and $\epsilon_{ijkt}$ in their distributions for each trial, 3 treatments (+ the untreated control), 3 dates ($t$=0, 6, 12), and 4 blocks
- Calculate $\lambda_{ijkt}$ from @eq-model_lambda,
- Draw values of $W_{ijkts}$ in its Poisson distribution for 10 plants ($s$=1, ..., 10)
- Calculate $Y_{ijkt}$ and $Z_{ijkt}$ from the Ws for each trial, treatment, date, block.
- Generate the eight data subsets corresponding to the scenarios defined in Table 3 (including all values of $W$, the generated values of $Y$ only, the generated values of $Z$ only, both $Y$ and $Z$ values but not $W$, the values of $Y$ in 50% of the trials, the values of $Z$ in 50% of the trials, the values of $Y$ in 50% of the trials and the values of $Z$ in the other 50%), 
- Fit the model (@eq-model_W - @eq-model_Z) to each of the data subsets according to the procedure described above based on MCMC.

At the end of this procedure, we get eight sets of estimated parameters, corresponding to the eight scenarios defined in Table 3. 
This procedure is repeated 974 times with each time a different seed between 0 and 999, thus generating eight series of 974 sets of estimated model parameters for each trial number.

For each number of trials and each scenario defined in Table 3, the accuracy of the estimated parameters $\gamma$ (from which depend the treatment efficacies) is evaluated by computing an absolute error, averaged over the three treatments ($j$=1 corresponding to the control) as:

$$
	E_{\gamma} = \frac{1}{2 \times 3}\sum\limits_{j = 2}^{4} \Big( \frac{|\gamma_{0j} - \hat{\gamma}_{0j}|}{|\gamma_{0j}|} + \frac{|\gamma_{1j} - \hat{\gamma}_{1j}|}{|\gamma_{1j}|}\Big)
$$ {#eq-E_gamma}

where the true parameter values are set equal to the posterior means computed with the real dataset, and the parameter estimates ($\hat{\gamma}_{0j}$ and $\hat{\gamma}_{1j}$) are the posterior means computed for the jth treatment. For each trial number and each scenario defined in Table 3, the 974 values of $E_{\gamma}$ obtained for the 974 generated data subsets are then averaged. The average values obtained for the eight scenarios are finally compared to determine the type of data leading to the most accurate estimated parameter values.

In addition, we compare the eight scenarios according to another criterion measuring the difference between the estimated efficacy values and the true efficacy value (averaged over the three pesticide treatments considered), as follows:

$$
	E_{\text{Ef}_{t}}\ = \frac{1}{3} \sum\limits_{j = 2}^4 \frac{|\text{Ef}_{jt} - \hat{\text{Ef}}_{jt}|} {|\text{Ef}_{jt}|}
$$ {#eq-E_efficacy}

where the true treatment efficacy is defined by @eq-Efficacy (setting the parameters $\gamma$s to the posterior means obtained with the real dataset) and the estimated efficacy ($\hat{\text{Ef}}_{jt}$) is the posterior mean computed with the simulated dataset. The 974 values of $E_{\text{Eft}}$ obtained from the 974 simulated datasets are then averaged for each trial number and each scenario. Finally, we evaluate the proportions of cases where the true best treatment (i.e., the treatment with the highest efficacy) is correctly identified.

In order to determine whether the difference of performance obtained with the types of data $Y$ and $Z$ depends on the pest abundance, we perform an additional series of simulations with three values for the model parameter $\alpha_0$, equal to $-1,\ 1$ and $2$, successively. These three values of $\alpha_0$ define three contrasted levels of pest abundance (the higher $\alpha_0$, the higher the abundance). We used the procedure outlined above considering only two scenarios of data availability, namely "100% Y" and "100% Z". This procedure is implemented with each value of $\alpha_0$ in turn. The results are used to compare the model performances using either $Y$ or $Z$ for parameter estimation, depending of the pest abundance specified by $\alpha_0$.

|Type of dataset| Description|
|---|---|
|100% W | W observations available in all the trials| 
|100% Y | Y observations available in all the trials|
|100% Z | Z observations available in all the trials|
|100% Y - 100 Z | Y and Z observations available in all the trials|
|50% Y | Y observations available in half of the trials|
|50% Z | Z observations available in half of the trials|
|50% Y / 50% Z | Y observations available in half of the trials and Z observations available in the other half of the trials|
|100% Z / 50% Y | Y observations available in half of the trials and Z observations available in all the trials|

: Eight scenarios compared using simulated data. {tbl-colwidths="[35,65]"}

The code used to perform the simulations is presented below.

```{r simulation-function}
#| echo: true
#| eval: true 
#| file: functions/simu_data.R 
```

\

::: {.callout-note}
The following code presents the inference for one seed. As the computing time is growing fast with the number of trials and the number of sampled values, we set here the number of trials to 10 (I = 10) and the number of adaptations and iterations to 2000.

Our simulation results are obtained by running this code for I = 10, 20, 40, 80, for all seeds between 0 and 999, with a number of adaptations and iterations equal to 36000. We used the Migale server from INRAE to run these simulations.
:::

```{r simulations, results = 'hide'}
#| echo: true
#| eval: false
#| file: scripts/simulations.R
```

# Results
## Results obtained with real data

```{r load_res_real_data, cache = FALSE, echo = FALSE}
resY = readRDS(file = "Files_for_code/Results/Real_data/res.Y.nadapt.150000.niter.3e+05.rds")
resYZ = readRDS(file = "Files_for_code/Results/Real_data/res.YhalfZhalf.nadapt.150000.niter.3e+05.rds") 
resYhalf = readRDS(file = "Files_for_code/Results/Real_data/res.Yhalf.nadapt.150000.niter.3e+05.rds")  
resZhalf = readRDS(file = "Files_for_code/Results/Real_data/res.Zhalf.nadapt.150000.niter.3e+05.rds") 
```

We present here the results obtained with real data. First, we check the convergence of the model for the scenarios defined in Table 2. We then compare the estimated values and the credibility intervals of the treatment efficacy obtained in the different scenarios.

### Model convergence and posterior distributions

@fig-two presents the Markov chains associated with the model parameters and treatment efficacies for the different scenarios. The x-axis presents the iteration number and the y-axis presents the sampled value. Results show that the chains are well mixed. @fig-three presents the Gelman-Rubin statistics associated with the model parameters and treatement efficacies as a function of the iterations, for the different scenarios. We observe that this statistics converges to 1, which indicates the convergence of the algorithm.

Table 4 gives a summary of the posterior distributions of the model parameters and treatment efficacies obtained for the "100% Y" scenario. The significantly positive value of $\alpha_1$ indicates that the aphid numbers tend to increase with time in untreated plots. The relatively high value of $\sigma_0$ (posterior mean equal to 1.87) reveals a strong variability in aphid numbers between trials. The posterior mean value of $\chi$ (0.27) suggests that the treatment efficacy varies across trials. The $\gamma_0$ parameter is negative for all three treatments, indicating a negative effect of the treatments on the aphid numbers at the time of pesticide spray. The Movento and Teppeki treatments have a similar effect with a posterior mean for $\gamma_0$ equal to -1.13 and -1.24, and a standard deviation equal to 0.12 and 0.11, respectively. The effect of treatment Mavrik Jet is weaker as its posterior mean for $\gamma_0$ is equal to -0.13 and its standard deviation is equal to 0.16. The $\gamma_1$ posterior means are negative for Movento and Teppeki (-0.14 and -0.15), suggesting that the effect of these treatments tend to increase with time, but the posterior mean value is positive for Mavrik Jet (= 0.24), suggesting that the effect of this treatment may decrease with time. However, the 95% credibility intervals of $\gamma_1$ include zero and these parameters are not very accurately estimated.

```{r figure2, cache = TRUE, out.width="100%", fig.height = 7, echo = FALSE}
#| label: fig-two
#| fig-cap: "Model convergence - Markov chain for the model parameters and treatment efficacies, in the scenarios '50% Y' (**A**),  '50% Y / 50% Z' (**B**), '100% Y' (**C**) and '50% Z' (**D**). The x-axis presents the iteration number and the y-axis presents the sampled value."

source(file = "functions/plot_chains.R")

options(warn = - 1)
col_background = "#e9e9e9";   col_text = "black"
cex = 0.85
nrow = 3
nbreaks = 3
strip_size = 5

fig2A = suppressMessages(plot_chains(resYhalf, nrow = nrow) + ylab("Sampled value") + scale_x_continuous(breaks = c(0, 1.5e4, 3e4))) + xlab("") +
	scale_y_continuous(n.breaks = nbreaks) + theme(strip.text = element_text(size = strip_size))
my_g2A <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("A", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

fig2B = suppressMessages(plot_chains(resYZ, nrow = nrow) + ylab("Sampled value") + scale_x_continuous(breaks = c(0, 1.5e4, 3e4))) + xlab("") +
	scale_y_continuous(n.breaks = nbreaks) + theme(strip.text = element_text(size = strip_size))
my_g2B <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("B", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

fig2C = suppressMessages(plot_chains(resY, nrow = nrow) + ylab("Sampled value") + scale_x_continuous(breaks = c(0, 1.5e4, 3e4))) + xlab("") +
	scale_y_continuous(n.breaks = nbreaks) + theme(strip.text = element_text(size = strip_size))
my_g2C <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("C", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

fig2D = suppressMessages(plot_chains(resZhalf, nrow = nrow) + ylab("Sampled value") + scale_x_continuous(breaks = c(0, 1.5e4, 3e4))) +
	scale_y_continuous(n.breaks = nbreaks) + theme(strip.text = element_text(size = strip_size), axis.title.x = element_text(margin = margin(t = 5)))
my_g2D <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("D", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

grid.arrange(my_g2A, fig2A, my_g2B, fig2B, my_g2C, fig2C, my_g2D, fig2D, heights = c(1,9,1,9,1,9,1,10))
```

\

```{r figure3, cache = TRUE, out.width="100%", fig.height = 7, echo = FALSE}
#| label: fig-three
#| fig-cap: "Model convergence - Gelman-Rubin statistics for the parameters of the model (@eq-model_W - @eq-model_Z) and for treatment efficacies (@eq-Efficacy), according to the scenarios 50% Y (**A**),  50% Y / 50% Z (**B**), 100% Y (**C**) and 50% Z (**D**). The x-axis presents the iteration number and the y-axis presents the Gelman-Rubin statistic."

source(file = "functions/gelman.plot2.R")

margey = 5
margex = 10
ncol = 9
strip_size = 5
breaks = c(1, 3, 5);   limits = c(1, 5)

fig3A = gelman.plot2(resYhalf, ncol = ncol) + 
    scale_x_continuous(breaks = c(2e5, 4e5)) + xlab("") +
	scale_y_continuous(limits = limits, breaks = breaks) +
    theme(axis.title.y = element_text(margin = margin(l = - margey, r = margey)), legend.position = "none", strip.text = element_text(size = strip_size))
my_g3A <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("A", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

fig3B = gelman.plot2(resYZ, ncol = ncol) + 
    scale_x_continuous(breaks = c(2e5, 4e5)) + xlab("") +   
	scale_y_continuous(limits = limits, breaks = breaks) +
    theme(axis.title.y = element_text(margin = margin(l = - margey, r = margey)), legend.position = "none", strip.text = element_text(size = strip_size))
my_g3B <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("B", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

fig3C = gelman.plot2(resY, ncol = ncol) + 
    scale_x_continuous(breaks = c(2e5, 4e5)) + xlab("") +    
	scale_y_continuous(limits = limits, breaks = breaks) +
    theme(axis.title.y = element_text(margin = margin(l = - margey, r = margey)), legend.position = "none", strip.text = element_text(size = strip_size)) 
my_g3C <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("C", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

fig3D = gelman.plot2(resZhalf, ncol = ncol) + 
    scale_x_continuous(breaks = c(2e5, 4e5))  + xlab("") +       
	scale_y_continuous(limits = limits, breaks = breaks) +
    theme(axis.title.y = element_text(margin = margin(l = - margey, r = margey)), strip.text = element_text(size = strip_size), plot.margin = margin(b = - 5, t = 6, r = 6, l = 6)) 
my_g3D <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("D", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

x_axis <- grobTree(textGrob("Last iteration in chain", x = 0.5, hjust = 0.5, gp = gpar(cex = 0.7)))
legend = cowplot::get_legend(fig3D)

grid.arrange(my_g3A, fig3A, my_g3B, fig3B, my_g3C, fig3C, my_g3D, fig3D + theme(legend.position = "none"), x_axis, legend, heights = c(1,9,1,9,1,9,1,9, 1, 2))
```
\

```{r table4, cache = TRUE, echo = FALSE}

tab4 = cbind(summary(resY)$statistics, summary(resY)$quantiles) %>% 
    as.data.frame %>%
    rownames_to_column(var = "Parameter") %>% select(- c(4, 5, c(7 : 9))) %>%
    mutate(Parameter = recode(Parameter, "gamma0[1]" = "gamma0 - untreated", "gamma0[2]" = "gamma0 - Mavrik Jet",
                                         "gamma0[3]" = "gamma0 - Movento", "gamma0[4]" = "gamma0 - Teppeki",
                                          "gamma1[1]" = "gamma1 - untreated", "gamma1[2]" = "gamma1 - Mavrik Jet",
                                         "gamma1[3]" = "gamma1 - Movento", "gamma1[4]" = "gamma1 - Teppeki"  )) %>%
    filter(!grepl("Eff", Parameter)) %>%

    mutate(Parameter = recode(Parameter, "alpha0" = "\u03B1\u2080",
                                         "alpha1" = "\u03B1\u2081",
                                         "chi" = "\u03C7",
                                         "eta" = "\u03B7",
                                         "sigma0" = "\u03C3\u2080")) %>%
    mutate(Parameter = gsub(x = Parameter, pattern = "gamma0", replacement = "\u03B3\u2080")) %>%
    mutate(Parameter = gsub(x = Parameter, pattern = "gamma1", replacement = "\u03B3\u2081")) %>%
    mutate_if(is.numeric, round, 2)

# re-ordering the parameters
tab4 = tab4[c(c(1 : 2), 13, c(3 : 12)), ]

rownames(tab4) = NULL

tab4 %>% 
  kbl(booktabs = TRUE, caption = "Summary of the posterior distributions obtained with the 100 Y scenario for the model parameters and treatment efficacies: posterior mean, standard deviation, 2.5 and 97.5 quantiles.") %>%
  kable_styling()
```

### Estimated values of pesticide treatment efficacies

@fig-four presents the posterior means and the 95% credibility intervals of treatment efficacies at 6 days (A) and 12 days (B) after pesticide spray, for the "100% Y", "50% Y / 50% Z", "50% Y" and "50% Z" scenarios. Different scenarios are indicated by different colors. The x-axis presents the efficacy and the y-axis presents the treatments. Overall, the results obtained are consistent across scenarios; Teppeki and Movento show higher mean efficacies than Mavrik Jet, and the credibility intervals are narrower for Teppeki and Movento than for Mavrik Jet in all scenarios. The credibility interval of the "100% Y" scenario is narrower than that of the "50% Y / 50% Z" scenario, which is itself narrower than that of the "50% Y" and "50% Z" scenarios. Table 5 quantifies the differences in the sizes of the credibility intervals and present the reduction percentage in the credibility interval sizes of the "100% Y", "50% Y / 50% Z" and "50% Z" scenarios, compared to the "50% Y" scenario, for all the treatment efficacies at 6 days (third column) and at 12 days (fourth column) after pesticide spray. A positive (negative) value corresponds to an increase (decrease) of the credibility interval size compared to "50% Y". For example, the credibility interval size obtained for the efficacy of Movento at 6 days is 40.5% smaller with the "100% Y" scenario than with the "50% Y" scenario. Overall, the credibility interval sizes obtained with the "100% Y" scenario are 25 to 45% smaller than those obtained with the "50% Y" scenario. This indicates that the accuracy of the estimated treatment efficacies is improved by doubling the number of Y observations. Results show that the credibility intervals are often larger with "50% Z" than with "50% Y", suggesting that better esimtations are obtained using Y than Z when only a limited number of data is available, at least in this case study. Interestingly, the sizes of the credibility intervals are smaller by about 25% with "50% Y / 50% Z" compared to "50% Y", showing that the combination of Y and Z observations collected in different trials in beneficial and lead to a reduction of the uncertainty in the estimated treatment efficacy. The latter result illustrates how the estimation of treatment efficacy could be improved by combining trials with prevalence data and trials with intensity data.

```{r figure4, cache = TRUE, echo=FALSE, out.width = "100%", fig.height = 2.6}
#| label: fig-four
#| fig-cap: "Estimated treatment efficacies after 6 days (**A**) and after 12 days (**B**), with their credibility intervals. Colors correspond to the different scenarios."

#######################################################################################################################################################

y1 = 0.075;   y2 = 0.225

# PR à 6 jours

df_resY = cbind(summary(resY)$statistics[1 : 3, ], summary(resY)$quantiles[1 : 3, ]) %>%
    as.data.frame %>% select(Mean, `2.5%`, `97.5%`) %>% rownames_to_column("Insecticide") %>%
    pivot_longer(cols = c(3, 4)) %>% rename(P = Mean) %>%
    mutate(name = recode(name, `2.5%` = "b_inf", `97.5%` = "b_sup")) %>%
    mutate(Insecticide = recode(Insecticide, "Eff[2,1]" = "Mavrik Jet", "Eff[3,1]" = "Movento", "Eff[4,1]" = "Teppeki"))

df_resYZ = cbind(summary(resYZ)$statistics[1 : 3, ], summary(resYZ)$quantiles[1 : 3, ]) %>%
    as.data.frame %>% select(Mean, `2.5%`, `97.5%`) %>% rownames_to_column("Insecticide") %>%
    pivot_longer(cols = c(3, 4)) %>% rename(P = Mean) %>%
    mutate(name = recode(name, `2.5%` = "b_inf", `97.5%` = "b_sup")) %>%
    mutate(Insecticide = recode(Insecticide, "Eff[2,1]" = "Mavrik Jet", "Eff[3,1]" = "Movento", "Eff[4,1]" = "Teppeki"))

df_resYhalf = cbind(summary(resYhalf)$statistics[1 : 3, ], summary(resYhalf)$quantiles[1 : 3, ]) %>%
    as.data.frame %>% select(Mean, `2.5%`, `97.5%`) %>% rownames_to_column("Insecticide") %>%
    pivot_longer(cols = c(3, 4)) %>% rename(P = Mean) %>%
    mutate(name = recode(name, `2.5%` = "b_inf", `97.5%` = "b_sup")) %>%
    mutate(Insecticide = recode(Insecticide, "Eff[2,1]" = "Mavrik Jet", "Eff[3,1]" = "Movento", "Eff[4,1]" = "Teppeki"))

df_resZhalf = cbind(summary(resZhalf)$statistics[1 : 3, ], summary(resZhalf)$quantiles[1 : 3, ]) %>%
    as.data.frame %>% select(Mean, `2.5%`, `97.5%`) %>% rownames_to_column("Insecticide") %>%
    pivot_longer(cols = c(3, 4)) %>% rename(P = Mean) %>%
    mutate(name = recode(name, `2.5%` = "b_inf", `97.5%` = "b_sup")) %>%
    mutate(Insecticide = recode(Insecticide, "Eff[2,1]" = "Mavrik Jet", "Eff[3,1]" = "Movento", "Eff[4,1]" = "Teppeki"))

Order = "binf"

df_IC = rbind(df_resYhalf %>% mutate(Data = "50% Y"), 
              df_resYZ %>% mutate(Data = "50% Y / 50% Z"),
              df_resY %>% mutate(Data = "100% Y"),
              df_resZhalf %>% mutate(Data = "50% Z"))

prod_rescale = df_resY %>% group_by(Insecticide) %>% summarise(P = ifelse(Order == "moyenne", max(P), min(value))) %>%
                           as.data.frame %>% arrange(P) %>% select(Insecticide) %>% as.matrix %>% as.vector

x = c(1 : length(prod_rescale));   names(x) = prod_rescale

df_IC_6 = df_IC %>% mutate(Ordonnee = recode(Insecticide, !!!x)) %>%
                      mutate(Ordonnee = ifelse(Data == "100% Y", Ordonnee + y2, 
                                               ifelse(Data == "50% Y / 50% Z", Ordonnee + y1,
                                                      ifelse(Data == "50% Y", Ordonnee - y1, Ordonnee - y2))),
                             jour = "6")

# calcul du pourcentage de réduction de l'IC par rapport au scenario 50% Y
df_len = df_IC %>% select(Insecticide, name, value, Data) %>% pivot_wider(names_from =  c(name)) %>% as.data.frame %>%
    mutate(IC_length = b_sup - b_inf) %>% arrange(Insecticide)

df_remp = df_len %>% filter(Data == "50% Y") %>% select(Insecticide, IC_length)
x  = df_remp$IC_length;   names(x) = df_remp$Insecticide

df_len = df_len %>% mutate(length50pcY = recode(Insecticide, !!!x)) %>%
    mutate(`For efficacy at 6 days` = (1 - (IC_length / length50pcY)) * (- 100));

df_len6 = df_len %>% rename(Insecticide = Insecticide) %>% select(Insecticide, Data, `For efficacy at 6 days`) %>% 
    filter(Data != "50% Y") %>% arrange(Data) %>% mutate_if(is.numeric, round, digits = 1)

#######################################################################################################################################################
# PR à 12 jours
df_resY = cbind(summary(resY)$statistics[4 : 6, ], summary(resY)$quantiles[4 : 6, ]) %>%
    as.data.frame %>% select(Mean, `2.5%`, `97.5%`) %>% rownames_to_column("Insecticide") %>%
    pivot_longer(cols = c(3, 4)) %>% rename(P = Mean) %>%
    mutate(name = recode(name, `2.5%` = "b_inf", `97.5%` = "b_sup")) %>%
    mutate(Insecticide = recode(Insecticide, "Eff[2,2]" = "Mavrik Jet", "Eff[3,2]" = "Movento", "Eff[4,2]" = "Teppeki"))

df_resYZ = cbind(summary(resYZ)$statistics[4 : 6, ], summary(resYZ)$quantiles[4 : 6, ]) %>%
    as.data.frame %>% select(Mean, `2.5%`, `97.5%`) %>% rownames_to_column("Insecticide") %>%
    pivot_longer(cols = c(3, 4)) %>% rename(P = Mean) %>%
    mutate(name = recode(name, `2.5%` = "b_inf", `97.5%` = "b_sup")) %>%
    mutate(Insecticide = recode(Insecticide, "Eff[2,2]" = "Mavrik Jet", "Eff[3,2]" = "Movento", "Eff[4,2]" = "Teppeki"))

df_resYhalf = cbind(summary(resYhalf)$statistics[4 : 6, ], summary(resYhalf)$quantiles[4 : 6, ]) %>%
    as.data.frame %>% select(Mean, `2.5%`, `97.5%`) %>% rownames_to_column("Insecticide") %>%
    pivot_longer(cols = c(3, 4)) %>% rename(P = Mean) %>%
    mutate(name = recode(name, `2.5%` = "b_inf", `97.5%` = "b_sup")) %>%
    mutate(Insecticide = recode(Insecticide, "Eff[2,2]" = "Mavrik Jet", "Eff[3,2]" = "Movento", "Eff[4,2]" = "Teppeki"))

df_resZhalf = cbind(summary(resZhalf)$statistics[4 : 6, ], summary(resZhalf)$quantiles[4 : 6, ]) %>%
    as.data.frame %>% select(Mean, `2.5%`, `97.5%`) %>% rownames_to_column("Insecticide") %>%
    pivot_longer(cols = c(3, 4)) %>% rename(P = Mean) %>%
    mutate(name = recode(name, `2.5%` = "b_inf", `97.5%` = "b_sup")) %>%
    mutate(Insecticide = recode(Insecticide, "Eff[2,2]" = "Mavrik Jet", "Eff[3,2]" = "Movento", "Eff[4,2]" = "Teppeki"))

Order = "binf"

df_IC = rbind(df_resYhalf %>% mutate(Data = "50% Y"), 
              df_resYZ %>% mutate(Data = "50% Y / 50% Z"),
              df_resY %>% mutate(Data = "100% Y"),
              df_resZhalf %>% mutate(Data = "50% Z"))

prod_rescale = df_resY %>% group_by(Insecticide) %>% summarise(P = ifelse(Order == "moyenne", max(P), min(value))) %>%
                           as.data.frame %>% arrange(P) %>% select(Insecticide) %>% as.matrix %>% as.vector

x = c(1 : length(prod_rescale));   names(x) = prod_rescale

df_IC_12 = df_IC %>% mutate(Ordonnee = recode(Insecticide, !!!x)) %>%
                      mutate(Ordonnee = ifelse(Data == "100% Y", Ordonnee + y2, 
                                               ifelse(Data == "50% Y / 50% Z", Ordonnee + y1,
                                                      ifelse(Data == "50% Y", Ordonnee - y1, Ordonnee - y2))),
                             jour = "12")

# calcul du pourcentage de réduction de l'IC par rapport au scenario 50% Y
df_len = df_IC %>% select(Insecticide, name, value, Data) %>% pivot_wider(names_from =  c(name)) %>% as.data.frame %>%
    mutate(IC_length = b_sup - b_inf) %>% arrange(Insecticide)

df_remp = df_len %>% filter(Data == "50% Y") %>% select(Insecticide, IC_length)
x  = df_remp$IC_length;   names(x) = df_remp$Insecticide

df_len = df_len %>% mutate(length50pcY = recode(Insecticide, !!!x)) %>%
    mutate(`For efficacy at 12 days` = (1 - (IC_length / length50pcY)) * (- 100));

df_len12 = df_len %>% rename(Insecticide = Insecticide) %>% select(Insecticide, Data, `For efficacy at 12 days`) %>% 
    filter(Data != "50% Y") %>% arrange(Data) %>% mutate_if(is.numeric, round, digits = 1)

#######################################################################################################################################################
df_IC = rbind(df_IC_6, df_IC_12) %>% mutate(jour = recode(jour, "6" = "A", "12" = "B"));

col = c("#9F248FFF", "#017A4AFF", "#F9791EFF", "#244579FF")   # c(paletteer_d("awtools::spalette", n = 5))[- c(2)]

ggplot(df_IC) + geom_point(aes(x = P, y = Ordonnee, color = Data), size = 1) +
    geom_line(aes(x = value, y = Ordonnee, group = Ordonnee, color = Data), size = 0.4) + 
    scale_color_manual(values = col, limits = c("100% Y", "50% Y / 50% Z", "50% Y", "50% Z")) + 
    scale_y_discrete(limits = prod_rescale) + 
    theme(legend.position = "bottom", legend.key.width = unit(1, 'cm'), legend.key.size = unit(0.4, "cm"))  + ylab("") +
    xlab("Treatment efficacy") + geom_vline(xintercept = 0, col = "#990033", size = 0.5, linetype = "dashed") +
    theme(axis.title.x = element_text(margin = margin(b = - 7, t = 5))) +
    facet_wrap(~ jour, ncol = 2, scales = "free_x")
```

```{r table5, cache = TRUE, echo = FALSE}

cbind(df_len6, df_len12 %>% select(- Data, - Insecticide)) %>% 
  kbl(booktabs = TRUE, caption = "Differences in the sizes of the 95 credibility intervals (CI) of the estimated treatment efficacies for the scenarios 50 Y / 50 Z, 50 Z and 100 Y, compared to 50 Y. The difference is given in percentage. A positive (negative) value indicates an increase (decrease) of the credibility interval size. The third column indicates differences for the efficacy at 6 days after pesticide spray, and the fourth column indicates the difference for the efficacy at 12 days.") %>% 
  kable_styling()
```

## Results obtained by simulation

```{r load_res_simulations, cache = FALSE, echo = FALSE}
df_col_simu = readRDS(file = "Files_for_code/Results/Simulations/df_col_simu.rds")
res_simu_sigma_1.87 = readRDS(file = "Files_for_code/Results/Simulations/res_simu_sigma_1.87.rds")

res_simu = res_simu_sigma_1.87

res_simu = res_simu %>% mutate(Type = recode(Type, "Y" = "100% Y", "Z" = "100% Z", "Zdemi" = "50% Z",
                                                                  "Ydemi" = "50% Y", "YdemiZdemi" = "50% Y / 50% Z", "ZYdemi" = "100% Z / 50% Y"),
                                         Erreur = recode(name, "MEgamma" = "A", "MEEf6" = "B", "MEEf12" = "C", "MEbest6" = "A", "MEbest12" = "B"),
                                         value = ifelse(grepl("best", name), value * 100, value))

df_col = df_col_simu

types = res_simu$Type %>% unique
x = df_col %>% filter(type %in% types) %>% select(col) %>% as.matrix %>% as.vector;   names(x) = types

res_simu = res_simu %>% mutate(Col = recode(Type, !!!x))
```

### Interest of combining trials with prevalence and trials with intensity

In this section, we consider the situation where only one type of observation is available per trial - pest prevalence or pest intensity. We compare the accuracy of the estimated parameters and estimated levels of treatment efficacy obtained by combining both types of trials compared to the results obtained using each set of trials separately.

The parameters used to generate the data are given in table 6.

```{r table6, cache = TRUE, echo = FALSE}

tab6 = data.frame(Parameters = c(

                    # alpha_0 et alpha_1
                    c("\u03B1\u2080", "\u03B1\u2081"),

                    # gamma_0
                    c("\u03B3\u2080\u2080", "\u03B3\u2080\u2081", "\u03B3\u2080\u2082", "\u03B3\u2080\u2083"),

                    # gamma_1
                    c("\u03B3\u2081\u2080", "\u03B3\u2081\u2081", "\u03B3\u2081\u2082", "\u03B3\u2081\u2083"),

                    # sigma_0, eta et chi
                    c("\u03C3\u2080", "\u03B7", "\u03C7")
                    ),
                  Values = c(alpha0, alpha1, gamma0, gamma1, sig0, eta, chi))

tab6 %>%
    t %>%
    kbl(booktabs = TRUE, caption = "Parameters used to generate virtual data.") %>%
    kable_styling()
```

@fig-five represents the $E_{\gamma}$ (@eq-E_gamma) (**A**), $E_{Ef_6}$ (@eq-E_efficacy) (**B**) and $E_{Ef_{12}}$ (@eq-E_efficacy) (**C**) evaluation criteria for the "50% Z", "50% Y" and "50% Y / 50% Z" scenarios (different scenarios are indicated by different colors. The x-axis presents the number of trials and the y-axis the value of the criterion, averaged over the simulated data sets. For each number of trials and for each criterion, we observe that scenario "50% Y / 50% Z" gives a more accurate estimate than scenario "50% Y" which itself gives a more accurate estimate than scenario "50% Z". For example, for the efficacy at 6 days with 40 trials, the mean absolute error of scenario "50% Y" is 10% less than the mean absolute error of scenario "50% Z" (0.38 vs 0.42). The mean absolute error of scenario "50% Y / 50% Z" is 35% less than that of scenario "50% Z" (0.26 vs 0.42). The values of the three criteria decrease with the number of trials. The $E_{\gamma}$ criterion decreases from 0.62 with 20 trials to 0.32 with 80 trials for the "50% Y / 50% Z" scenario. A value of 20 trials is therefore not sufficient to obtain an accurate estimate of the parameters.

```{r figure5, cache = TRUE, out.width="100%", fig.height = 2.5, echo = FALSE}
#| label: fig-five
#| fig-cap: "Values of the $E_{\\gamma}$ (@eq-E_gamma) (**A**), $E_{Ef_6}$ (@eq-E_efficacy) (**B**) and $E_{Ef_{12}}$ (@eq-E_efficacy) (**C**) mean absolute error criteria for the '50% Z', '50% Y' and '50% Y / 50% Z' scenarios. The x-axis presents the number of trials and the y-axis presents the mean absolute error, averaged over the 974 simulated datasets. Different colors correspond to different scenarios."

types = c("50% Y", "50% Y / 50% Z", "50% Z")
res_temp = res_simu %>% filter(Type %in% types)
col_temp = df_col %>% arrange(type) %>% filter(type %in% types) %>% select(col) %>% as.matrix %>% as.vector

ggplot(res_temp %>% filter(!grepl("best", name))) + geom_point(aes(x = I, y = value, color = Type), size = 1) +
    geom_line(aes(x = I, y = value, color = Type), size = 0.2) + xlab("Number of trials") +
    facet_wrap(~ Erreur, nrow = 1, scales = "free") + theme(legend.position = "bottom") +
    ylab("Mean absolute error") + theme(legend.title = element_blank(), axis.title.x = element_text(margin = margin(t = 5, b = -8))) +
    scale_color_manual(values = col_temp)
```

@fig-six presents the percentages of cases where the best treatment at 6 days (A) and 12 days (B) has been correctly identified for the "50% Y", "50% Z" and "50% Y / 50% Z" scenarios. The x-axis presents the number of trials and the y-axis the percentage of cases where the treatment identification is correct. In general, the best treatment is better identified when the number of trials increases. With the "50% Y / 50% Z" scenario, the best treatment at 6 days is well identified in 69% of cases with 20 trials and in 85% of cases with 80 trials. For each number of trials, the percentage of correctly identification is higher for the "50% Y / 50% Z" scenario than for the other two, and the scenario "50% Y" generally gives better results than the scenario "50% Z", except at 6 days with 20 trials. For example, at 12 days after treatment and with 40 trials, the percentage of correct identification is 5% higher with scenario "50% Y - 50% Z" than with scenario "50% Y" (78 vs 73), and 4% higher with the scenario "50% Y" than with scenario "50% Z" (73 vs 69). These results show the interest of combining prevalence and intensity data for assessing the efficacy of treatments and identifying the best treatments.

```{r figure6, cache = TRUE, out.width="100%", fig.height = 3, echo = FALSE}
#| label: fig-six
#| fig-cap: "Comparison of proportion cases where the best treatment is correctly identified in the '50% Z', '50% Y' and '50% Y / 50% Z' scenarios. The x-axis represents the number of trials and the y-axis represents the percentage of cases where the best treatment has been correctly identified at 6 days (A) and 12 days (B), over the 974 simulated datasets. Different colors correspond to different scenarios."

ggplot(res_temp %>% filter(grepl("best", name))) + geom_point(aes(x = I, y = value, color = Type), size = 1) +
    geom_line(aes(x = I, y = value, color = Type), size = 0.2) + xlab("Number of trials") +
    facet_wrap(~ Erreur, nrow = 1, scales = "free") + theme(legend.position = "bottom") +
    ylab("Best treatment identification percentage") + theme(legend.title = element_blank(), axis.title.x = element_text(margin = margin(t = 5, b = - 8))) +
    scale_color_manual(values = col_temp)
```

### Interest of adding intensity when prevalence is measured in all trials

We now consider a situation where prevalence is measured in each trial and intensity is measured in only some of these trials. We compare the results obtained when the data are combined and when they are used separately. As the prevalence data are usually more accessible in practice and the intensity data more costly, it is important to evaluate the interest of adding intensity data in the statistical analysis.

 The parameters used to generate the data are the same as in 3.2.1.

 @fig-seven presents the evaluation criteria $E_{\gamma}$ (Fig 7A), $E_{Ef_6}$ (Fig 7B) and $E_{Ef_{12}}$ (Fig. 7C) for the scenarios "100% Z", "50% Y", "100% Z / 50% Y" and "50% Y / 50% Z". The x-axis presents the number of trials and the y-axis presents the value of the criterion, averaged over the number of simulated data sets. Results show that the mean absolute errors are lower in scenarios "100% Z / 50% Y" and "50% Y / 50% Z" than in "100% Z", and that the mean absolute errors are lower in the "100% Z" scenario than in the "50% Y" scenario. For example, considering the treatment efficacy at 12 days with 40 trials (Fig. 7C), the mean absolute errors are 13% lower in scenarios "100% Z / 50% Y" and "50% Y / 50% Z" than in "100% Z" (0.30 vs 0.34), and the mean absolute error is 11% lower in "100% Z" than in "50% Y" (0.34 vs 0.38). Clearly, adding intensity data to prevalence data improves the accuracy of the estimations. The mean absolute errors decrease with the number of trials. For example, the $E_{\gamma}$ criterion decreases from 0.62 with 20 trials to 0.32 with 80 trials for the "50% Y / 50% Z" scenario. As noted above, 20 trials is clearly not sufficient to obtain accurate results.

```{r figure7, cache = TRUE, out.width="100%", fig.height = 2.5, echo = FALSE}
#| label: fig-seven
#| fig-cap: "Values of $E_{\\gamma}$ (@eq-E_gamma) (**A**), $E_{Ef_6}$ (@eq-E_efficacy) (**B**) and $E_{Ef_{12}}$ (@eq-E_efficacy) (**C**) for the '100% Z', '50% Y', '100% Z / 50% Y' and '50% Y / 50% Z' scenarios. The x-axis presents the number of trials and the y-axis presents the absolute error averaged over the 974 simulated datasets. Different colors correspond to different scenarios."

types = c("50% Y", "100% Z", "100% Z / 50% Y", "50% Y / 50% Z")
res_temp = res_simu %>% filter(Type %in% types )
col_temp = df_col %>% arrange(type) %>% filter(type %in% types) %>% select(col) %>% as.matrix %>% as.vector

ggplot(res_temp %>% filter(!grepl("best", name))) + geom_point(aes(x = I, y = value, color = Type), size = 1) +
    geom_line(aes(x = I, y = value, color = Type), size = 0.2) + xlab("Number of trials") +
    facet_wrap(~ Erreur, nrow = 1, scales = "free") + theme(legend.position = "bottom") +
    ylab("Mean absolute error") + theme(legend.title = element_blank(), axis.title.x = element_text(margin = margin(t = 5, b = - 8))) +
    scale_color_manual(values = col_temp)
```

### Is it better to measure intensity or prevalence in new pest surveys?

In order to optimize the design of new pest surveys that might be conducted in the future, we determine which type of observations should be favored. For that purpose, we compare the results obtained with the "100% Y", "100% Z", "100% Y / 100% Z" and "100% W" scenarios, for different values of $\alpha_0$ that defines the average number of infested plants. With $\alpha_0$ = -1, the proportion of infested plants is generally much lower than one, while with $\alpha_0 = 2$, 100% of plants are generally infested. The case $\alpha_0$ = 1 leads to intermediate levels of infestation.

The three parameter sets used to generate the data are given in Table 7 and are labeled A, B and C.

```{r table7, cache = TRUE, echo = FALSE}

tab7 = data.frame(Parameters = c(
                    # alpha_0 et alpha_1
                    c("\u03B1\u2080", "\u03B1\u2081"),

                    # gamma_0
                    c("\u03B3\u2080\u2080", "\u03B3\u2080\u2081", "\u03B3\u2080\u2082", "\u03B3\u2080\u2083"),

                    # gamma_1
                    c("\u03B3\u2081\u2080", "\u03B3\u2081\u2081", "\u03B3\u2081\u2082", "\u03B3\u2081\u2083"),

                    # sigma_0, eta et chi
                    c("\u03C3\u2080", "\u03B7", "\u03C7")
                    ),

                  "Values set A" = c(-1, alpha1, gamma0, gamma1, sig0, eta, chi),
                  "Values set B" = c(1, alpha1, gamma0, gamma1, sig0, eta, chi),
                  "Values set C" = c(2, alpha1, gamma0, gamma1, sig0, eta, chi)
                  )

tab7 %>%
    t %>% 
    `rownames<-`(c("Set", "A", "B", "C")) %>% 
    kbl(booktabs = TRUE, caption = "Parameters considered for the design of future pest surveys.") %>%
    column_spec(2, bold = TRUE) %>%
    kable_styling()
```

@fig-height (A.1, B.1 and C.1) shows the mean absolute error $E_{\gamma}$ (@eq-E_gamma) as a function of the number of trials for the four scenarios "100% Y", "100% Z", "100% Y / 100% Z" and "100% W". @fig-height (A.2, B.2 and C.2) shows the distributions of infested plants with 40 trials corresponding to the three values of $\alpha_0$ reported in Table 7.
In case A (Table 7), the distribution of Z is such that Z is rarely close to 1 and often lower than 0.5 (@fig-height A.2). In case C, the distribution of Z is such that Z is often very close to 1 (100% of plants infested). Case B is intermediate. The accuracy of the estimated values of the model parameters $\gamma$ is better with scenario "100% Y" than with scenario "100% Z", for all number of trials. The advantage of "100% Y" is stronger in case of high pest prevalence (i.e., cases B and C) but very small in case of low pest prevalence (case A). For example, with 20 trials, the mean absolute error is 27% lower in the scenario "100% Y" than in "100% Z" for parameter set C (0.55 vs. 0.75), 10% lower for parameter set B (0.55 vs. 0.62), and not different for parameter set A (0.64). The "100% W" scenario leads to similar results as "100% Y", regardless of $\alpha_0$ and the number of trials. Results obtained with "100% Y / 100% Z" are generally similar to those obtained with "100% Y" and "100% W" but better than those obtained with the scenario "100% Z" in cases B and C. Here again, results show that 20 trials are not sufficient to obtain accurate parameter estimates.

```{r figure8, cache = FALSE, out.width="100%", fig.height = 6, echo = FALSE}
#| label: fig-height
#| fig-cap: "Comparison of the '100% Y', '100% Z', '100% Y / 100% Z' and '100% W' scenarios according to the distribution of $Z$ and the number of trials, using the $E_{\\gamma}$ criterion (@eq-E_gamma). **A**, **B** and **C** correspond to different $Z$ distributions which are given by A.2, B.2 and C.2 (distribution for a number of trials equal to 40). A, B and C respectively correspond to $\\alpha_0 =$ -1, 1 and 2. The details of the simulation parameters are given in table 7. A1, B1 and C1 represent the absolute error $E_{\\gamma}$ averaged over the 974 simulated datasets as a function of the number of trials. Colors correspond to the different scenarios."

res_simu_q3_1 = readRDS(file = "Files_for_code/Results/Simulations/res_simu_q3_1.rds");   
res_simu_q3_2 = readRDS(file = "Files_for_code/Results/Simulations/res_simu_q3_2.rds")

res_simu_q3_1 = res_simu_q3_1 %>% mutate(Type = recode(Type, "100% Y - 100% Z" = "100% Y / 100% Z"))

types = res_simu_q3_1$Type %>% unique
col = df_col %>% arrange(type) %>% filter(type %in% types) %>% select(col) %>% as.matrix %>% as.vector

g1 = suppressWarnings(ggplot(res_simu_q3_1) + geom_point(aes(x = I, y = Mean_MAE, color = Type), size = 1) +
              geom_line(aes(x = I, y = Mean_MAE, color = Type), size = 0.2) +
    facet_wrap(~ alpha0, ncol = 1, labeller = label_wrap_gen(multi_line = FALSE)) + 
    ylab(TeX("Mean relative absolute error for $\\gamma$")) + scale_color_manual(values = col[c(1, 2, 3, 4)]) + theme(plot.margin = margin(l = 0)) +
    xlab("Number of trials") + theme(legend.position = "bottom", plot.margin = margin(t = 0, l = 0)))

legend = cowplot::get_legend(g1)

g2 = suppressWarnings(ggplot(res_simu_q3_2) + geom_histogram(aes(Z), stat = "count", fill = "#4345a1") + facet_wrap(~ alpha0, ncol = 1) + 
    ylab("Number of observations") + theme(plot.margin = margin(r = 0, l = 15, t = 0)) + xlab("Number of infested beets"))

suppressWarnings(do.call("grid.arrange", c(list(legend), list(g1  + theme(legend.position = "none"), g2), list(ncol = 2, layout_matrix = rbind(c(2, 3), c(1, 1)), heights = c(1, 0.2)))))
```

# Conclusion

In order to evaluate pest treatment efficacy, numerous trials are conducted to monitor pest prevalence and intensity. Quite often, only one type of data is available and, when both prevalence and intensity are available, they are usually analysed separately. In this paper, we proposed an alternative approach based on a hierarchical statistical model able to analyze intensity and prevalence data, simultaneously.

We successfully applied the model to a real dataset including prevalence and incidence data collected to evaluate three pesticide treatments against aphids in sugar beets. The model was fitted to this datased using a Markov chain Monte Carlo algorithm, and convergence was quickly achieved after a few thousands iterations. Results showed that the use of both prevalence and intensity data led to a substantial reduction of the uncertainty in the parameter estimates, compared to the use of a single type of data.

Results obtained from simulated data confirmed that, when pest prevalence and pest intensity are collected separately in different trials, the model parameters are more accurately estimated combining both prevalence and intensity trials than using one type of trials only. We also found that, when prevalence data are collected in all trials and intensity data are collected in a subset of trials, estimations and pest treatment ranking are more accurate using both types of data than using prevalence data only. Moreover, when only one type of observation can be collected in a pest survey or in an experimental trial, our analysis indicates that it is usually better to collect intensity data than prevalence data, especially in situations where all or most of the plants are expected to be infested. Finally, our simulations show that it is unlikely to obtain accurate results with fewer than 40 trials when assessing the efficacy of pest control treatments based on prevalence and intensity data.

The model and codes presented in this paper can be easily implemented to analyze a diversity of pest trials and surveys including prevalence and/or intensity data.

# Author contributions {.unnumbered}

AF and DM designed the study. AF performed the computations. AF and DM wrote the paper.

# Funding {.unnumbered}

This work was partly funded by the project SEPIM (PNRI) and by the RMT SDMAA.

# Data availability {.unnumbered}

Simulated data and model parameters are available without restriction. The original experimental data may be available under request.

# Acknowledgements {.unnumbered}

We are grateful to Anabelle Laurent, Elma Raaijmakers, Kathleen Antoons and to the institute ITB (https://www.itbfr.org/) for their comments on this project.

We are grateful to the INRAE MIGALE bioinformatics facility (MIGALE, INRAE, 2020. Migale bioinformatics Facility, doi: 10.15454/1.5572390655343293E12) for providing help and/or computing and/or storage resources.

# References {.unnumbered}

### 2023-09-08 Article/scripts/inference_example_real_data.R

@@ -1,0 +1,106 @@
+
+
+# Jags code for the model  #################################################
+modelstringYZ = "
+    model {
+
+        # Likelihood #####################################################
+        for (i in 1:Q){
+            Y[i] ~ dpois(N[i] * lb[i])
+            Z[i] ~ dbinom(pi[i], N[i])
+
+            log(lb[i]) = beta0[ID[i]] + gamma0[INSEC[i]] + (alpha1 + 
+                         gamma1[INSEC[i]]) * TIME[i] + u[ST[i]] + epsi[i]
+
+            pi[i] = 1 - exp(- lb[i])
+            epsi[i] ~ dnorm(0, pi_eps)
+        }
+
+        for (j in 1:K){
+            beta0[j] ~ dnorm(alpha0, tau0)
+        }
+
+        for (c in 1:M){
+            u[c] ~ dnorm(0, invchi)
+        }
+
+        gamma0[1] = 0
+        gamma1[1] = 0
+
+        # Priors #########################################################
+        for (s in 2:L){
+            gamma0[s] ~ dnorm(0, 0.001)
+            gamma1[s] ~ dnorm(0, 0.001)
+        }
+
+        alpha0 ~ dnorm(0, 0.001)
+        alpha1 ~ dnorm(0, 0.001)
+        sigma0 ~ dunif(0, 10)
+        chi ~ dunif(0, 10)
+        eta ~ dunif(0, 10)
+
+        # Derived Quantities #############################################
+        tau0 = pow(sigma0, -2)
+        invchi = pow(chi, -2)
+        pi_eps = pow(eta, -2)
+
+        for (h in 2:L){
+            for(t in 1 : T){
+                Eff[h, t]  = (1 - exp(gamma0[h] + gamma1[h] * 
+                             TIME_unique[t])) * 100
+            }
+        }  
+    }
+"
+
+writeLines(modelstringYZ, con  =  "Files_for_code/modelYZ.txt")
+############################################################################
+
+
+# Inference example on the extract of the real dataset #####################
+load(file = "Files_for_code/real_data_extract.Rdata")
+data = real_data_extract %>% 
+  mutate(tscaled = scale(DPT), st = paste(ID, Insecticide))
+
+# Building scenarios -------------------------------------------------------
+scenarioY = data %>% mutate(Z = NA)
[…]

### 2023-09-08 Review/simu_data_NegB.R

@@ -1,0 +1,52 @@
+simu_data_NegB <- function(I, K, S, r, alpha_0, alpha_1, gamma_0, gamma_1, X_t, sigma2, chi2){
+        
+    J = length(gamma_0)   # number of treatments 
+    T = length(X_t)   # number of observation date
+
+    trials = paste("trial", c(1 : I))
+    treatments = paste("treatment", c(1 : J))
+    times = paste("time", c(1 : T))
+    blocks = paste("block", c(1 : K))
+    beets = paste("beet", c(1 : S))
+
+    data_simu = expand.grid(trial = trials, treatment = treatments, time = times, block = blocks, beet = beets) %>%
+      mutate(trial_treatment = paste(trial, treatment))
+
+    names(gamma_0) = treatments
+    names(gamma_1) = treatments
+
+    names(X_t) = times
+
+    beta = rnorm(I, sd = sqrt(sigma2));   names(beta) = trials
+    u_ij = rnorm(I * J, sd = sqrt(chi2));   names(u_ij) = unique(data_simu$trial_treatment)
+
+
+    data_simu = data_simu %>%
+        mutate(r = r) %>%
+        mutate(N = S) %>%
+        mutate(alpha_0 = alpha_0) %>%
+        mutate(alpha_1 = alpha_1) %>%
+        mutate(gamma_0 = recode(treatment, !!!gamma_0),
+               gamma_1 = recode(treatment, !!!gamma_1),
+               X_t = recode(time, !!!X_t),
+               beta = recode(trial, !!!beta),
+               u_ij = recode(trial_treatment, !!!u_ij)) %>%
+
+        mutate(X_t = scale(X_t)) %>%
+
+        mutate(lambda = exp(alpha_0 + beta + gamma_0 + (alpha_1 + gamma_1) * X_t + u_ij)) %>%
+
+        mutate(W = rnbinom(n = I * J * K * T * S, 
+                           mu = lambda,
+                           size = r)) %>%
+
+        group_by(trial, time, treatment, block, X_t, N) %>%
+        summarise(Y = sum(W), Z = sum(W > 0), .groups = "drop") %>%
+
+        mutate(trial_treatment = paste(trial, treatment)) %>%
+
+        mutate(ligne = row_number())
+
+    
+    return(data_simu)
+}

### 2023-09-08 Article/Article.qmd
change in notation for scenarios

@@
 dataset, which includes both trials of figure 1B (2020 - B1A97 ; 2020 - 
-u1CwE). It is  a demo for the "50% Y / 50% Z" scenario and we set here the 
+u1CwE). It is  a demo for the "50% Y - 50% Z" scenario and we set here the 
 number of adaptation and iteration to 2000 in order to reduce computation 
@@
 We consider four datasets including trials with observations of $Y$, with observations of $Z$, or with both types of observation in different proportions (Table 2).
-The dataset "100% Y" includes Y data collected in the 32 trials.
+The dataset "100% Y - 0% Z" includes Y data collected in the 32 trials.
 The dataset "50%Y" includes Y data collected in the 17 trials for which no Z observation is available.
@@
 |---------|:-----|
-| 100% Y      | Y observations available in the 32 trials   |
-| 50% Y     | Y observations available in 17 trials and no Z  | 
-| 50% Z       | Z observations available in 15 trials and no Y    | 
-| 50% Y / 50% Z       | Y observations available in 17 trials and Z observations available in the other 15 trials   |
+| 100% Y - 0% Z      | Y observations available in the 32 trials and no Z   |
+| 50% Y - 0% Z     | Y observations available in 17 trials and no Z  | 
+| 50% Z - 0% Y       | Z observations available in 15 trials and no Y    | 
+| 50% Y - 50% Z       | Y observations available in 17 trials and Z observations available in the other 15 trials   |
 
@@
 We define three numbers of trials, equal to 20, 40 and 80, successively.
-For data simulations, the model parameters are set equal to those estimated from the real dataset "100% Y" defined in Table 2 (posterior means).
+For data simulations, the model parameters are set equal to those estimated from the real dataset "100% Y - 0% Z" defined in Table 2 (posterior means).
 For each number of trials, we generate virtual data from the model (@eq-model_W - @eq-model_Z) and estimate the model parameters, according to the following procedure:
@@
 These three values of $\alpha_0$ define three contrasted levels of pest abundance (the higher $\alpha_0$, the higher the abundance).
-We used the procedure outlined above considering only two scenarios of data availability, namely "100% Y" and "100% Z".
+We used the procedure outlined above considering only two scenarios of data availability, namely "100% Y - 0% Z" and "100% Z - 0% Y".
 This procedure is implemented with each value of $\alpha_0$ in turn.
@@
 |100% W | W observations available in all the trials| 
-|100% Y | Y observations available in all the trials|
-|100% Z | Z observations available in all the trials|
+|100% Y - 0% Z | Y observations available in all the trials|
+|100% Z - 0% Y | Z observations available in all the trials|
 |100% Y - 100 Z | Y and Z observations available in all the trials|
-|50% Y | Y observations available in half of the trials|
-|50% Z | Z observations available in half of the trials|
-|50% Y / 50% Z | Y observations available in half of the trials and Z observations available in the other half of the trials|
-|100% Z / 50% Y | Y observations available in half of the trials and Z observations available in all the trials|
+|50% Y - 0% Z | Y observations available in half of the trials|
+|50% Z - 0% Y | Z observations available in half of the trials|
+|50% Y - 50% Z | Y observations available in half of the trials and Z observations available in the other half of the trials|
+|100% Z - 50% Y | Y observations available in half of the trials and Z observations available in all the trials|
 
@@
 
-Table 4 gives a summary of the posterior distributions of the model parameters and treatment efficacies obtained for the "100% Y" scenario.
+Table 4 gives a summary of the posterior distributions of the model parameters and treatment efficacies obtained for the "100% Y - 0% Z" scenario.
 The significantly positive value of $\alpha_1$ indicates that the aphid numbers tend to increase with time in untreated plots.
@@
 #| label: fig-two
-#| fig-cap: "Model convergence - Markov chain for the model parameters and treatment efficacies, in the scenarios '50% Y' (**A**),  '50% Y / 50% Z' (**B**), '100% Y' (**C**) and '50% Z' (**D**).
+#| fig-cap: "Model convergence - Markov chain for the model parameters and treatment efficacies, in the scenarios '50% Y - 0% Z' (**A**),  '50% Y - 50% Z' (**B**), '100% Y - 0% Z' (**C**) and '50% Z - 0% Y' (**D**).
 The x-axis presents the iteration number and the y-axis presents the sampled value."
@@
 #| label: fig-three
-#| fig-cap: "Model convergence - Gelman-Rubin statistics for the parameters of the model (@eq-model_W - @eq-model_Z) and for treatment efficacies (@eq-Efficacy), according to the scenarios 50% Y (**A**),  50% Y / 50% Z (**B**), 100% Y (**C**) and 50% Z (**D**).
+#| fig-cap: "Model convergence - Gelman-Rubin statistics for the parameters of the model (@eq-model_W - @eq-model_Z) and for treatment efficacies (@eq-Efficacy), according to the scenarios '50% Y - 0% Z' (**A**),  '50% Y - 50% Z' (**B**), '100% Y - 0% Z' (**C**) and '50% Z - 0% Y'(**D**).
 The x-axis presents the iteration number and the y-axis presents the Gelman-Rubin statistic."
@@
 
-@fig-four presents the posterior means and the 95% credibility intervals of treatment efficacies at 6 days (A) and 12 days (B) after pesticide spray, for the "100% Y", "50% Y / 50% Z", "50% Y" and "50% Z" scenarios.
+@fig-four presents the posterior means and the 95% credibility intervals of treatment efficacies at 6 days (A) and 12 days (B) after pesticide spray, for the "100% Y - 0% Z", "50% Y - 50% Z", "50% Y - 0% Z" and "50% Z - 0% Y" scenarios.
 Different scenarios are indicated by different colors.
@@
 Overall, the results obtained are consistent across scenarios; Teppeki and Movento show higher mean efficacies than Mavrik Jet, and the credibility intervals are narrower for Teppeki and Movento than for Mavrik Jet in all scenarios.
-The credibility interval of the "100% Y" scenario is narrower than that of the "50% Y / 50% Z" scenario, which is itself narrower than that of the "50% Y" and "50% Z" scenarios.
-Table 5 quantifies the differences in the sizes of the credibility intervals and present the reduction percentage in the credibility interval sizes of the "100% Y", "50% Y / 50% Z" and "50% Z" scenarios, compared to the "50% Y" scenario, for all the treatment efficacies at 6 days (third column) and at 12 days (fourth column) after pesticide spray.
-A positive (negative) value corresponds to an increase (decrease) of the credibility interval size compared to "50% Y".
-For example, the credibility interval size obtained for the efficacy of Movento at 6 days is 40.5% smaller with the "100% Y" scenario than with the "50% Y" scenario.
-Overall, the credibility interval sizes obtained with the "100% Y" scenario are 25 to 45% smaller than those obtained with the "50% Y" scenario.
+The credibility interval of the "100% Y - 0% Z" scenario is narrower than that of the "50% Y - 50% Z" scenario, which is itself narrower than that of the "50% Y - 0% Z" and "50% Z - 0% Y" scenarios.
+Table 5 quantifies the differences in the sizes of the credibility intervals and present the reduction percentage in the credibility interval sizes of the "100% Y - 0% Z", "50% Y - 50% Z" and "50% Z - 0% Y" scenarios, compared to the "50% Y - 0% Z" scenario, for all the treatment efficacies at 6 days (third column) and at 12 days (fourth column) after pesticide spray.
+A positive (negative) value corresponds to an increase (decrease) of the credibility interval size compared to "50% Y - 0% Z".
+For example, the credibility interval size obtained for the efficacy of Movento at 6 days is 40.5% smaller with the "100% Y - 0% Z" scenario than with the "50% Y - 0% Z" scenario.
+Overall, the credibility interval sizes obtained with the "100% Y - 0% Z" scenario are 25 to 45% smaller than those obtained with the "50% Y - 0% Z" scenario.
 This indicates that the accuracy of the estimated treatment efficacies is improved by doubling the number of Y observations.
-Results show that the credibility intervals are often larger with "50% Z" than with "50% Y", suggesting that better esimtations are obtained using Y than Z when only a limited number of data is available, at least in this case study.
-Interestingly, the sizes of the credibility intervals are smaller by about 25% with "50% Y / 50% Z" compared to "50% Y", showing that the combination of Y and Z observations collected in different trials in beneficial and lead to a reduction of the uncertainty in the estimated treatment efficacy.
+Results show that the credibility intervals are often larger with "50% Z - 0% Y" than with "50% Y - 0% Z", suggesting that better esimtations are obtained using Y than Z when only a limited number of data is available, at least in this case study.
+Interestingly, the sizes of the credibility intervals are smaller by about 25% with "50% Y - 50% Z" compared to "50% Y - 0% Z", showing that the combination of Y and Z observations collected in different trials in beneficial and lead to a reduction of the uncertainty in the estimated treatment efficacy.
 The latter result illustrates how the estimation of treatment efficacy could be improved by combining trials with prevalence data and trials with intensity data.
@@
 
-df_IC = rbind(df_resYhalf %>% mutate(Data = "50% Y"), 
-              df_resYZ %>% mutate(Data = "50% Y / 50% Z"),
-              df_resY %>% mutate(Data = "100% Y"),
-              df_resZhalf %>% mutate(Data = "50% Z"))
+df_IC = rbind(df_resYhalf %>% mutate(Data = "50% Y - 0% Z"), 
+              df_resYZ %>% mutate(Data = "50% Y - 50% Z"),
+              df_resY %>% mutate(Data = "100% Y - 0% Z"),
+              df_resZhalf %>% mutate(Data = "50% Z - 0% Y"))
 
@@
 df_IC_6 = df_IC %>% mutate(Ordonnee = recode(Insecticide, !!!x)) %>%
-                      mutate(Ordonnee = ifelse(Data == "100% Y", Ordonnee + y2, 
-                                               ifelse(Data == "50% Y / 50% Z", Ordonnee + y1,
-                                                      ifelse(Data == "50% Y", Ordonnee - y1, Ordonnee - y2))),
+                      mutate(Ordonnee = ifelse(Data == "100% Y - 0% Z", Ordonnee + y2, 
+                                               ifelse(Data == "50% Y - 50% Z", Ordonnee + y1,
+                                                      ifelse(Data == "50% Y - 0% Z", Ordonnee - y1, Ordonnee - y2))),
                              jour = "6")
 
-# calcul du pourcentage de réduction de l'IC par rapport au scenario 50% Y
+# calcul du pourcentage de réduction de l'IC par rapport au scenario 50% Y - 0% Z
 df_len = df_IC %>% select(Insecticide, name, value, Data) %>% pivot_wider(names_from =  c(name)) %>% as.data.frame %>%
@@
 
-df_remp = df_len %>% filter(Data == "50% Y") %>% select(Insecticide, IC_length)
+df_remp = df_len %>% filter(Data == "50% Y - 0% Z") %>% select(Insecticide, IC_length)
 x  = df_remp$IC_length;   names(x) = df_remp$Insecticide
@@
 df_len6 = df_len %>% rename(Insecticide = Insecticide) %>% select(Insecticide, Data, `For efficacy at 6 days`) %>% 
-    filter(Data != "50% Y") %>% arrange(Data) %>% mutate_if(is.numeric, round, digits = 1)
+    filter(Data != "50% Y - 0% Z") %>% arrange(Data) %>% mutate_if(is.numeric, round, digits = 1)
 
@@
 df_IC_12 = df_IC %>% mutate(Ordonnee = recode(Insecticide, !!!x)) %>%
-                      mutate(Ordonnee = ifelse(Data == "100% Y", Ordonnee + y2, 
-                                               ifelse(Data == "50% Y / 50% Z", Ordonnee + y1,
-                                                      ifelse(Data == "50% Y", Ordonnee - y1, Ordonnee - y2))),
+                      mutate(Ordonnee = ifelse(Data == "100% Y - 0% Z", Ordonnee + y2, 
+                                               ifelse(Data == "50% Y - 50% Z", Ordonnee + y1,
+                                                      ifelse(Data == "50% Y - 0% Z", Ordonnee - y1, Ordonnee - y2))),
                              jour = "12")
 
-# calcul du pourcentage de réduction de l'IC par rapport au scenario 50% Y
+# calcul du pourcentage de réduction de l'IC par rapport au scenario 50% Y - 0% Z
 df_len = df_IC %>% select(Insecticide, name, value, Data) %>% pivot_wider(names_from =  c(name)) %>% as.data.frame %>%
@@
 df_len12 = df_len %>% rename(Insecticide = Insecticide) %>% select(Insecticide, Data, `For efficacy at 12 days`) %>% 
-    filter(Data != "50% Y") %>% arrange(Data) %>% mutate_if(is.numeric, round, digits = 1)
+    filter(Data != "50% Y - 0% Z") %>% arrange(Data) %>% mutate_if(is.numeric, round, digits = 1)
 
@@
     geom_line(aes(x = value, y = Ordonnee, group = Ordonnee, color = Data), size = 0.4) + 
-    scale_color_manual(values = col, limits = c("100% Y", "50% Y / 50% Z", "50% Y", "50% Z")) + 
+    scale_color_manual(values = col, limits = c("100% Y - 0% Z", "50% Y - 50% Z", "50% Y - 0% Z", "50% Z - 0% Y")) + 
     scale_y_discrete(limits = prod_rescale) + 
@@
 
-res_simu = res_simu %>% mutate(Type = recode(Type, "Y" = "100% Y", "Z" = "100% Z", "Zdemi" = "50% Z",
-                                                                  "Ydemi" = "50% Y", "YdemiZdemi" = "50% Y / 50% Z", "ZYdemi" = "100% Z / 50% Y"),
+res_simu = res_simu %>% mutate(Type = recode(Type, "Y" = "100% Y - 0% Z", "Z" = "100% Z - 0% Y", "Zdemi" = "50% Z - 0% Y",
+                                                                  "Ydemi" = "50% Y - 0% Z", "YdemiZdemi" = "50% Y - 50% Z", "ZYdemi" = "100% Z - 50% Y"),
                                          Erreur = recode(name, "MEgamma" = "A", "MEEf6" = "B", "MEEf12" = "C", "MEbest6" = "A", "MEbest12" = "B"),
@@
 
-@fig-five represents the $E_{\gamma}$ (@eq-E_gamma) (**A**), $E_{Ef_6}$ (@eq-E_efficacy) (**B**) and $E_{Ef_{12}}$ (@eq-E_efficacy) (**C**) evaluation criteria for the "50% Z", "50% Y" and "50% Y / 50% Z" scenarios (different scenarios are indicated by different colors.
+@fig-five represents the $E_{\gamma}$ (@eq-E_gamma) (**A**), $E_{Ef_6}$ (@eq-E_efficacy) (**B**) and $E_{Ef_{12}}$ (@eq-E_efficacy) (**C**) evaluation criteria for the "50% Z - 0% Y", "50% Y - 0% Z" and "50% Y - 50% Z" scenarios (different scenarios are indicated by different colors.
 The x-axis presents the number of trials and the y-axis the value of the criterion, averaged over the simulated data sets.
-For each number of trials and for each criterion, we observe that scenario "50% Y / 50% Z" gives a more accurate estimate than scenario "50% Y" which itself gives a more accurate estimate than scenario "50% Z".
-For example, for the efficacy at 6 days with 40 trials, the mean absolute error of scenario "50% Y" is 10% less than the mean absolute error of scenario "50% Z" (0.38 vs 0.42).
-The mean absolute error of scenario "50% Y / 50% Z" is 35% less than that of scenario "50% Z" (0.26 vs 0.42).
+For each number of trials and for each criterion, we observe that scenario "50% Y - 50% Z" gives a more accurate estimate than scenario "50% Y - 0% Z" which itself gives a more accurate estimate than scenario "50% Z - 0% Y".
+For example, for the efficacy at 6 days with 40 trials, the mean absolute error of scenario "50% Y - 0% Z" is 10% less than the mean absolute error of scenario "50% Z - 0% Y" (0.38 vs 0.42).
+The mean absolute error of scenario "50% Y - 50% Z" is 35% less than that of scenario "50% Z - 0% Y" (0.26 vs 0.42).
 The values of the three criteria decrease with the number of trials.
-The $E_{\gamma}$ criterion decreases from 0.62 with 20 trials to 0.32 with 80 trials for the "50% Y / 50% Z" scenario.
+The $E_{\gamma}$ criterion decreases from 0.62 with 20 trials to 0.32 with 80 trials for the "50% Y - 50% Z" scenario.
 A value of 20 trials is therefore not sufficient to obtain an accurate estimate of the parameters.
@@
 #| label: fig-five
-#| fig-cap: "Values of the $E_{\\gamma}$ (@eq-E_gamma) (**A**), $E_{Ef_6}$ (@eq-E_efficacy) (**B**) and $E_{Ef_{12}}$ (@eq-E_efficacy) (**C**) mean absolute error criteria for the '50% Z', '50% Y' and '50% Y / 50% Z' scenarios.
+#| fig-cap: "Values of the $E_{\\gamma}$ (@eq-E_gamma) (**A**), $E_{Ef_6}$ (@eq-E_efficacy) (**B**) and $E_{Ef_{12}}$ (@eq-E_efficacy) (**C**) mean absolute error criteria for the '50% Z - 0% Y', '50% Y' and '50% Y - 50% Z' scenarios.
 The x-axis presents the number of trials and the y-axis presents the mean absolute error, averaged over the 974 simulated datasets.
@@
 
-types = c("50% Y", "50% Y / 50% Z", "50% Z")
+types = c("50% Y - 0% Z", "50% Y - 50% Z", "50% Z - 0% Y")
 res_temp = res_simu %>% filter(Type %in% types)
@@
 
-@fig-six presents the percentages of cases where the best treatment at 6 days (A) and 12 days (B) has been correctly identified for the "50% Y", "50% Z" and "50% Y / 50% Z" scenarios.
+@fig-six presents the percentages of cases where the best treatment at 6 days (A) and 12 days (B) has been correctly identified for the "50% Y - 0% Z", "50% Z - 0% Y" and "50% Y - 50% Z" scenarios.
 The x-axis presents the number of trials and the y-axis the percentage of cases where the treatment identification is correct.
 In general, the best treatment is better identified when the number of trials increases.
-With the "50% Y / 50% Z" scenario, the best treatment at 6 days is well identified in 69% of cases with 20 trials and in 85% of cases with 80 trials.
-For each number of trials, the percentage of correctly identification is higher for the "50% Y / 50% Z" scenario than for the other two, and the scenario "50% Y" generally gives better results than the scenario "50% Z", except at 6 days with 20 trials.
-For example, at 12 days after treatment and with 40 trials, the percentage of correct identification is 5% higher with scenario "50% Y - 50% Z" than with scenario "50% Y" (78 vs 73), and 4% higher with the scenario "50% Y" than with scenario "50% Z" (73 vs 69).
+With the "50% Y - 50% Z" scenario, the best treatment at 6 days is well identified in 69% of cases with 20 trials and in 85% of cases with 80 trials.
+For each number of trials, the percentage of correctly identification is higher for the "50% Y - 50% Z" scenario than for the other two, and the scenario "50% Y - 0% Z" generally gives better results than the scenario "50% Z - 0% Y", except at 6 days with 20 trials.
+For example, at 12 days after treatment and with 40 trials, the percentage of correct identification is 5% higher with scenario "50% Y - 50% Z" than with scenario "50% Y - 0% Z" (78 vs 73), and 4% higher with the scenario "50% Y - 0% Z" than with scenario "50% Z - 0% Y" (73 vs 69).
 These results show the interest of combining prevalence and intensity data for assessing the efficacy of treatments and identifying the best treatments.
@@
 #| label: fig-six
-#| fig-cap: "Comparison of proportion cases where the best treatment is correctly identified in the '50% Z', '50% Y' and '50% Y / 50% Z' scenarios.
+#| fig-cap: "Comparison of proportion cases where the best treatment is correctly identified in the '50% Z - 0% Y', '50% Y' and '50% Y - 50% Z' scenarios.
 The x-axis represents the number of trials and the y-axis represents the percentage of cases where the best treatment has been correctly identified at 6 days (A) and 12 days (B), over the 974 simulated datasets.
@@
  @fig-seven presents the evaluation criteria $E_{\gamma}$ (Fig 7A), $E_{Ef_6}$ (Fig 7B) and $E_{Ef_{12}}$ (Fig.
-7C) for the scenarios "100% Z", "50% Y", "100% Z / 50% Y" and "50% Y / 50% Z".
+7C) for the scenarios "100% Z - 0% Y", "50% Y - 0% Z", "100% Z - 50% Y" and "50% Y - 50% Z".
 The x-axis presents the number of trials and the y-axis presents the value of the criterion, averaged over the number of simulated data sets.
-Results show that the mean absolute errors are lower in scenarios "100% Z / 50% Y" and "50% Y / 50% Z" than in "100% Z", and that the mean absolute errors are lower in the "100% Z" scenario than in the "50% Y" scenario.
+Results show that the mean absolute errors are lower in scenarios "100% Z - 50% Y" and "50% Y - 50% Z" than in "100% Z - 0% Y", and that the mean absolute errors are lower in the "100% Z - 0% Y" scenario than in the "50% Y - 0% Z" scenario.
 For example, considering the treatment efficacy at 12 days with 40 trials (Fig.
-7C), the mean absolute errors are 13% lower in scenarios "100% Z / 50% Y" and "50% Y / 50% Z" than in "100% Z" (0.30 vs 0.34), and the mean absolute error is 11% lower in "100% Z" than in "50% Y" (0.34 vs 0.38).
+7C), the mean absolute errors are 13% lower in scenarios "100% Z - 50% Y" and "50% Y - 50% Z" than in "100% Z - 0% Y" (0.30 vs 0.34), and the mean absolute error is 11% lower in "100% Z - 0% Y" than in "50% Y - 0% Z" (0.34 vs 0.38).
 Clearly, adding intensity data to prevalence data improves the accuracy of the estimations.
 The mean absolute errors decrease with the number of trials.
-For example, the $E_{\gamma}$ criterion decreases from 0.62 with 20 trials to 0.32 with 80 trials for the "50% Y / 50% Z" scenario.
+For example, the $E_{\gamma}$ criterion decreases from 0.62 with 20 trials to 0.32 with 80 trials for the "50% Y - 50% Z" scenario.
 As noted above, 20 trials is clearly not sufficient to obtain accurate results.
@@
 #| label: fig-seven
-#| fig-cap: "Values of $E_{\\gamma}$ (@eq-E_gamma) (**A**), $E_{Ef_6}$ (@eq-E_efficacy) (**B**) and $E_{Ef_{12}}$ (@eq-E_efficacy) (**C**) for the '100% Z', '50% Y', '100% Z / 50% Y' and '50% Y / 50% Z' scenarios.
+#| fig-cap: "Values of $E_{\\gamma}$ (@eq-E_gamma) (**A**), $E_{Ef_6}$ (@eq-E_efficacy) (**B**) and $E_{Ef_{12}}$ (@eq-E_efficacy) (**C**) for the '100% Z - 0% Y', '50% Y', '100% Z - 50% Y' and '50% Y - 50% Z' scenarios.
 The x-axis presents the number of trials and the y-axis presents the absolute error averaged over the 974 simulated datasets.
@@
 
-types = c("50% Y", "100% Z", "100% Z / 50% Y", "50% Y / 50% Z")
+types = c("50% Y - 0% Z", "100% Z - 0% Y", "100% Z - 50% Y", "50% Y - 50% Z")
 res_temp = res_simu %>% filter(Type %in% types )
@@
 In order to optimize the design of new pest surveys that might be conducted in the future, we determine which type of observations should be favored.
-For that purpose, we compare the results obtained with the "100% Y", "100% Z", "100% Y / 100% Z" and "100% W" scenarios, for different values of $\alpha_0$ that defines the average number of infested plants.
+For that purpose, we compare the results obtained with the "100% Y - 0% Z", "100% Z - 0% Y", "100% Y / 100% Z" and "100% W" scenarios, for different values of $\alpha_0$ that defines the average number of infested plants.
 With $\alpha_0$ = -1, the proportion of infested plants is generally much lower than one, while with $\alpha_0 = 2$, 100% of plants are generally infested.
@@
 
-@fig-height (A.1, B.1 and C.1) shows the mean absolute error $E_{\gamma}$ (@eq-E_gamma) as a function of the number of trials for the four scenarios "100% Y", "100% Z", "100% Y / 100% Z" and "100% W".
+@fig-height (A.1, B.1 and C.1) shows the mean absolute error $E_{\gamma}$ (@eq-E_gamma) as a function of the number of trials for the four scenarios "100% Y - 0% Z", "100% Z - 0% Y", "100% Y / 100% Z" and "100% W".
 @fig-height (A.2, B.2 and C.2) shows the distributions of infested plants with 40 trials corresponding to the three values of $\alpha_0$ reported in Table 7.
@@
 Case B is intermediate.
-The accuracy of the estimated values of the model parameters $\gamma$ is better with scenario "100% Y" than with scenario "100% Z", for all number of trials.
-The advantage of "100% Y" is stronger in case of high pest prevalence (i.e., cases B and C) but very small in case of low pest prevalence (case A).
-For example, with 20 trials, the mean absolute error is 27% lower in the scenario "100% Y" than in "100% Z" for parameter set C (0.55 vs.
+The accuracy of the estimated values of the model parameters $\gamma$ is better with scenario "100% Y - 0% Z" than with scenario "100% Z - 0% Y", for all number of trials.
+The advantage of "100% Y - 0% Z" is stronger in case of high pest prevalence (i.e., cases B and C) but very small in case of low pest prevalence (case A).
+For example, with 20 trials, the mean absolute error is 27% lower in the scenario "100% Y - 0% Z" than in "100% Z - 0% Y" for parameter set C (0.55 vs.
 0.75), 10% lower for parameter set B (0.55 vs.
 0.62), and not different for parameter set A (0.64).
-The "100% W" scenario leads to similar results as "100% Y", regardless of $\alpha_0$ and the number of trials.
-Results obtained with "100% Y / 100% Z" are generally similar to those obtained with "100% Y" and "100% W" but better than those obtained with the scenario "100% Z" in cases B and C.
+The "100% W" scenario leads to similar results as "100% Y - 0% Z", regardless of $\alpha_0$ and the number of trials.
+Results obtained with "100% Y / 100% Z" are generally similar to those obtained with "100% Y - 0% Z" and "100% W" but better than those obtained with the scenario "100% Z - 0% Y" in cases B and C.
 Here again, results show that 20 trials are not sufficient to obtain accurate parameter estimates.
@@
 #| label: fig-height
-#| fig-cap: "Comparison of the '100% Y', '100% Z', '100% Y / 100% Z' and '100% W' scenarios according to the distribution of $Z$ and the number of trials, using the $E_{\\gamma}$ criterion (@eq-E_gamma).
+#| fig-cap: "Comparison of the '100% Y - 0% Z', '100% Z - 0% Y', '100% Y / 100% Z' and '100% W' scenarios according to the distribution of $Z$ and the number of trials, using the $E_{\\gamma}$ criterion (@eq-E_gamma).
 **A**, **B** and **C** correspond to different $Z$ distributions which are given by A.2, B.2 and C.2 (distribution for a number of trials equal to 40).

### 2023-09-08 Article/scripts/simulations.R

@@ -12,9 +12,9 @@ sig0 = 1.87;   chi = 0.27;   eta = 0.98
 ############################################################################
 
 # Building scenarios #######################################################
-# Scenarios "50% Y" and "50% Z" are obtained from scenarios "100% Y" and 
-# "100% Z", respectively. For example "50% Y" scenario with 40 trials 
-# corresponds to "100% Y" with 20 trials.
+# Scenarios "50% Y - 0% Z" and "50% Z - 0% Y" are obtained from scenarios "100% Y - 0% Z" and 
+# "100% Z - 0% Y", respectively. For example "50% Y - 0% Z" scenario with 40 trials 
+# corresponds to "100% Y - 0% Z" with 20 trials.
 
 seed = 1;   I = 10
 data = suppressMessages(simu_data(seed = seed, I = I))

### 2023-09-08 Review/response_strategy.Rmd
-

@@
 .question {
-  text-indent: 5em;
   text-align: justify;
@@
 
-.indented_response {
-  text-indent: 5em;
-  color: #000080;
+.response{
+  color: #145805;
   text-align: justify;
@@
 
-.response {
+.response_strategy {
   color: #000080;
@@
   margin-bottom: 30px;
-  margin-left: 40px
 }
@@
   margin-bottom: 30px;
-  margin-left: 40px
 } 
@@
 
-::: indented_response
+::: response_strategy
 Ajouter des numéros de lignes dans mes fichiers.
@@
 
-::: indented_response         
+::: response_strategy         
 Ajouter une phrase dans la conclusion pour souligner ce point.
+:::
+
+::: response
+We added the following sentece in the conclusion : 
 :::
@@
 
-::: indented_response         
+::: response_strategy         
 Ce commentaire remet en question le modèle que l'on utilise et propose d'en utiliser un autre : la négative binomiale.
@@
 
+::: response
 [paragraphe biblio pour justifier notre choix]
@@
 
-$\begin{align}&\log\ \lambda_{ijkt} = \alpha_0 + \beta_{0i} + \gamma_{0j}  + (\alpha_1 + \gamma_{1j})\ X_t + u_{ij}\label{eq:test}\tag{1}\end{align}$
+$$\log\ \lambda_{ijkt} = \alpha_0 + \beta_{0i} + \gamma_{0j}  + (\alpha_1 + \gamma_{1j})\ X_t + u_{ij}$$
 
@@
 ```
+:::
 
@@
 
-::: response
+::: response_strategy
 Ce commentaire fait référence à cette phrase (dans l'introduction) : "measuring intensity is indeed often more time demanding than measuring prevalence, in particular when the pest individuals are small, numerous, and difficult to detect." Je ne comprends pas ce commentaire.
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à la phrase : "Recently, neonicotinoids were recognized as presenting high risks for the environment with a negative impact a wide range of non-target organisms"
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à la phrase : "and this familly of pesticides had been banned in several European countries"
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à la phrase : "Consequently, for a given pest treatment, some of trials may report prevalence data while others report intensity data"
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à la phrase : "while others report intensity data or both type of data"
@@
 
-  ::: response
+  ::: response_strategy
   les deux will en questions sont dans la phrase suivante : "It is unclear whether the simultaneous analysis of prevalence and intensity data will increase the accuracy of the estimated treatment efficacy compared to the use of a single type of data, and whether this will increase the probability of identifying the most efficient treatments" =\> faire le remplacement
@@
 
-::: response
+::: response_strategy
 Le reviewer fait référence à cette phrase : "Based on simulations, we then quantify the reduction of mean absolute errors in the estimated treatment efficacies induced by the combination of prevalence and incidence data compared to the use of a single type of data."
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à la phrase : "Data were collected in 32 field trials conducted in France, Belgium and Netherlands to compare several treatments"
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à la phrase : "Intensity and prevalence were monitored at different dates during the growing season."
@@
 
-::: response
+::: response_strategy
 =\> supprimer ces deux phrases
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à la phrase : "Then, assuming the Ws independent, we have:"
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à la phrase : "The different quantities used by the model are defined in Table 1."
@@
 
-::: response
+::: response_strategy
 Oui le nombre de plantes échantillonnées ne varie que selon les essais.
@@
 
-::: response
+::: response_strategy
 Je ne comprends pas ce commentaire, mais il m'a fait voir que la définition du temps n'est pas claire, je propose de remplacer X_t par t
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à la phrase "The model parameters were estimated using a Bayesian inference with a Markov chain Monte-Carlo method."
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à "and we centered the time variable $t$ to facilitate the convergence."
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à "The following code presents the inference on an extract fo the real 
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à "Likelyood" dans le modèle jags
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à "As the calculus time is growing fast" dans un commentaire du code des simulations
@@
 
-  ::: response
+  ::: response_strategy
   faité référence à "Our simulations results are obtained" dans le même commentaire.
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à "for assessing the efficacy of treatments and indentifying"
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à "and convergence was quickly achieved after a few thoushands iterations."
@@
 
-  ::: response
+  ::: response_strategy
   fait référence à "intensity data let to a substantial reduction of the uncertainty"
@@
 
-::: response         
+::: response_strategy         
 => Lire ces articles et voir si on peut y faire référence dans l’introduction
@@
 
-::: response
+::: response_strategy
 Ce commentaire fait référence à la partie suivante :
@@
 
-::: response
+::: response_strategy
 paramètre lié au site qui sont random, on ne veux pas faire d'inférence site par site, on veut faire une inférence pour la population de site, globale, choix qui dépend de l'obejctif de l'inférence, par rapport à la population de site
@@
 
-::: response
+::: response_strategy
+
+On ne connait pas le coût d'un essai où l'on mesure Y et le coût d'un essai où l'on mesure Z, on ne peut donc pas savoir quels scénarios considérer pour faire une comparaison sur la base des coûts.
+Le fait de comparer [50% Y - 0% Z] et [0% Y - 50% Z] montre simplement que la mesure de Y apporte plus de précision dans l'estimation que la mesure de Z (à nombre d'observations égale).
+
+Cependant ce commentaire me fait voir qu'il y a un problème dans l'article : la partie 3.2.3 "Is it better to measure intensity or prevalence in new pest surveys ?".
+Je pense que pour bien répondre à cette question il faudrait connaitre les coûts des différents scénarios.
+
 =\> Pour moi ce n'était pas le but de l'article d'approfondir cette question du coût et de l'optimisation qui en découle, étant donné que l'on a pas cette information.
@@
 
-#### D.1.
+#### D.1. &#9989;
 
@@
 
+::: response_strategy         
+=> faire la modification proposée
+:::
+
 ::: response 
-=> faire la modification proposée
+We made the change, it correspond to the commit "change in notation for scenarios" (dfbaa65).
+:::
+
+::: rouge
+Ne faudrait-il pas en plus normaliser la notation de la façon suivante : toujours Y en premier et Z en deuxième. Exemple "50% Y - 0% Z", "0% Y - 50% Z", plutôt que "50% Y - 0% Z", "50% Z - 0% Y".
 :::
@@
 
-::: response         
-=\> On ne peut pas faire ça car on ne dispose des Z que dans 15 essais sur les 32 (paragraphe 2.1)
+::: response_strategy         
+Expliquer que ce n'est pas possible car on ne dispose des Z que dans 15 essais sur les 32 (paragraphe 2.1)
 :::
 
+::: response
+We could not consider all the scenarios defined in Table 3 for the real data because we only have data for Z in 15 out of the 32 trials (see paragraph 2.1, "The number of infested plants (prevalence) was measured as well, but only in 15 trials out of 32").
+Therefore, we were unable to consider the scenarios "100% Z - 0% Y," "100% Y - 100% Z," and "100% Z - 50% Y." We also did not consider the scenario "100% W" because W is not measured (only the sum of aphids on the N sugar beets in the sample is reported).
+:::
+
+::: question
 Based on D0) why not consider more intermediate levels of Y : [25%Y - 100% Z], ...
+:::
+
+::: response_strategy
+Expliquer que l'objectif n'était pas de faire une optimisation de design, rajouter une phrase quelque part pour souligner que notre modèle pourra être utiliser pour faire de l'optimisation de design.
+:::
 
 ::: response
-on voulait surtout illustrer le principe des modèle et montrer que le design a un impact, et que notre modèle peut etre appliqué pour de l'optimisation
+We did not consider more intermediate scenarios because our goal was not to perform an experimental design optimization but simply to demonstrate that it is possible to combine Y and Z and that it is advantageous to do so when only Z is measured in certain trials.
+
+To emphasize one of the benefits of our model being experimental design optimization, we have added the following sentence:
+:::
+
+::: rouge
+Rajouter une phrase pour dire que notre modèle pourra être utilisé pour faire de l'optimisation de design.
 :::
@@
 
-::: response         
-il n'y pas de design optimal, il faut un point de départ, l'optimum dépend du parametre des modèles, on a fait des simus sur la base des paramètres inférés sur le s données réelles qui correspondent à des conditions spécifiques : on peux optimiser un design futur
+::: response_strategy         
+Je ne suis pas sur que le nombre de plantes soit un paramètre important.
+Mon intuition est qu'il est équivalent au nombre de sites.
+Par exemple je pense que deux sites où on mesure Z sur 20 plantes est équivalent à 4 sites où on mesure Z sur 10 plantes.
+Le nombre de plantes N pourrait cependant faire partie d'un problème d'optimisation sous contraintes dans lequel on veut par exemple un minimum de site pour couvrir un nombre suffisant de situation environnemental (météo, composition de la terre, présence de pucerons, ...).
 
-C'est vrai, plus le nombre de plantes est grand, plus la précision que Z apporte est grande. On ne l'a pas considéré pour des raisons de simplicité et de temps de calculs.
+On pourrait par exemple, étant donné $N_Y$ la taille d'échantillon pour laquelle on mesure l'intensité, chercher $N_Z$ la taille d'échantillon pour laquelle on mesure la prévalence qui soit telle que la précision obtenue avec l'intensité soit égale à la précision obtenue avec la prévalence.
 
-Stratégie de réponse : proposer d'en parler dans la conclusion, dire que cela pourrait faire partie d'un problème d'optimisation.
-On pourrait par exemple, étant donné N_y la taille d'échantillon pour laquelle on mesure l'intensité, chercher N_z la taille d'échantillon pour laquelle on mesure la prévalence qui soit telle que la précision obtenue avec l'intensité soit égale à la précision obtenue avec la prévalence.
-
-notre objectif n'éatit pas de faire une optimisation absolue du modèle,
+Faire à peu près la même réponse que pour D.2.2 : expliquer que l'objectif n'était pas faire de l'optimisation de design, mais que cela est possible en particulier en considérant N comme un paramètre à optimiser.
+Rajouter une phrase quelque part pour en parler.
 :::
@@
 
-::: response         
+::: response_strategy         
 Oui, voir la réponse précédente, il doit exister un $N_z = f(N_y)$ tel que la précision obtenue avec $Y$ soit égale à celle obtenue avec $Z$.
@@
 
-::: response         
+::: response_strategy         
 =\> Oui, stratégie de réponse : parler du temps de calculs pour justifier le nombre limité de scénarios considérés
@@
 
-::: response         
+::: response_strategy         
 =\> Oui, ces résultats sont basés sur un seul extrait du jeu de données
@@
 
-::: response
+::: response_strategy
 done, j'ai mis les données nécessaire aux figures dans /data/
@@
 
-::: response
+::: response_strategy
 J'ai fait ça pour les tables 4, 5, 6 et 7. 
@@
 
-::: response
+::: response_strategy
 done, j'ai juste installer le package renv et j'ai exécuté la commande renv::init() à la racine du dossier mysubmission.
@@
 
-::: response
+::: response_strategy
 cf commit "Points 5 and 6 of the reproductibility issue on github" (3c13239edfa017f6deac8feb6110d8b257542121) sur la branche correction_2.
@@
 
-::: response
+::: response_strategy
 cf commit "Points 5 and 6 of the reproductibility issue on github" (3c13239edfa017f6deac8feb6110d8b257542121) sur la branche correction_2
@@
 
-::: response
+::: response_strategy
 J'ai changé tous les .Rdata en .rds.

### 2023-09-08 Review/response_strategy.Rmd
-

@@
 Le nombre de plantes N pourrait cependant faire partie d'un problème d'optimisation sous contraintes dans lequel on veut par exemple un minimum de site pour couvrir un nombre suffisant de situation environnemental (météo, composition de la terre, présence de pucerons, ...).
+See [here](#optimisation) .
 
@@
 
+::: response
+Yes, the larger N is, the more informative Z becomes, and N could effectively be a part of an experimental design optimization problem.
+As mentioned in our response to comment D.2., our objective here was not to conduct an optimization of the design.
+However, we do propose to address this in the conclusion, and we have added the following sentence to it:
+:::
+
+::: rouge 
+Ajouter la phrase en question
+:::
+
 ::: question
@@
 ::: response_strategy         
-Oui, voir la réponse précédente, il doit exister un $N_z = f(N_y)$ tel que la précision obtenue avec $Y$ soit égale à celle obtenue avec $Z$.
+Oui, il doit exister un $N_Z$ fonction de $N_Y$, $N_Z = f(N_Y)$, tel que la précision obtenue avec $Y$ soit égale à celle obtenue avec $Z$.
+Il faudrait ensuite comparer le coût entre mesure de Y sur $N_Y$ betteraves et mesure de $Z$ sur $N_Z$ betteraves pour déterminer la meilleure option.
 
-Stratégie de réponse : proposer d’en parler dans la conclusion
+Rajouter une phrase dans la conclusion pour souligner ce point.
+:::
+
+::: response         
+Yes, there must exist an $N_Z$ that is a function of $N_Y$, where $N_Z = f(N_Y)$, such that the precision obtained with $Y$ is equal to that obtained with $Z$.
+Then, it would be necessary to compare the cost between measuring Y on $N_Y$ sugar beets and measuring $Z$ on $N_Z$ sugar beets to determine the better option.
+
+We have added the following sentence to the conclusion to emphasize this point:
 :::
@@
 
-## Problème d'optimisation
+## Problème d'optimisation {#optimisation}
 

### 2023-09-08 Review/response_strategy.Rmd
-

@@
     facet_wrap(~ model)
-```
-
-```{r, cache = TRUE}
-df_prediction %>%
-    summarise(MSE = sum(error), .by = model) %>% kbl() %>% kable_styling()
-```
-
-```{r, cache = TRUE}
-df_prediction %>%
-    summarise(MSE = sum(error), .by = model)
 ```
@@
 ::: response_strategy         
-=\> Oui, stratégie de réponse : parler du temps de calculs pour justifier le nombre limité de scénarios considérés
+Oui, stratégie de réponse : parler du temps de calculs pour justifier le nombre limité de scénarios considérés, en profiter pour citer migale.
+:::
+
+::: response
+Yes, we have added the following sentence at the end of section 2.2.3 (Material and Method / Model / Simulations):
+"These simulations required a significant amount of computation time and were conducted on the INRAE MIGALE server."
+
+And we have removed the following sentence from the note associated with the code on simulations :
+"We used the Migale server from INRAE to run these simulations".
+:::
+
+::: rouge
+Ajouter les phrases, rajouter la citation de Migale 
 :::

### 2023-09-09 Article/Article.qmd
R2 F - add sentence relative to the computation time of the simulations
R2 minor comment c - correction de la dernière phrase de l'avant dernier paragraphe de la partie 2.2.2

@@
 The dataset "50% $Y$ - 50% $Z$" includes $Y$ data collected in 17 trials and $Z$ data collected in the other 15 trials.
-The later dataset does include any trial reporting both $Y$ and $Z$ data.
+The latter dataset does not include any trial reporting both $Y$ and $Z$ data.
 
@@
 
-The code used to perform the simulations is presented below.
+These simulations required a significant amount of computation time and were conducted on the INRAE MIGALE server. The code used to perform them is presented below.
 
@@
 Our simulation results are obtained by running this code for I = 10, 20, 40, 80, for all seeds between 0 and 999, with a number of adaptations and iterations equal to 36000.
-We used the Migale server from INRAE to run these simulations.
 :::
